---
  title: 'Get Features Meta Data'
  author: "Daniel Antiporta"
  date: "`r format(Sys.time(), '%d %B %Y')`"
  output: 
    html_document:
      toc: false
      toc_depth: 3
---

```{r, include = FALSE}
rm(list = ls())
knitr::opts_chunk$set(include = TRUE, comment = NA, cache = TRUE, 
                      message = FALSE, warning = FALSE)

```

* Define project folder `712-final_project` path. That is, modify `project.dir` string below; once it points to your `712-final_project` folder location, all other stuff below would work. 

```{r}
user.name<-Sys.info()[7]
if(user.name=="antiporta") project.dir <- "/Users/antiporta/Dropbox/712-final_project/"
if(user.name=="dantipor") project.dir <- "C://Users//dantipor//Dropbox//712-final_project/"
if(user.name=="mkaras") project.dir <- "/Users/mkaras/Dropbox/JHU/711-ADV_DATA_SCIENCE/712-final_project/"
library(rvest)
library(ggplot2)
library(dplyr)
library(future)
library(readr)
library(stringr)
```

## Read `vector` with package name

```{r}
path.tmp <- file.path(project.dir, "data/pkg_name_SUBSET")
out.path <- file.path(project.dir, "data/pkg_first_release_urls_DA.csv")
release_urls_DA <- read.csv(out.path, stringsAsFactors = FALSE)
pkg_name_vec <- release_urls_DA$name
```

## Get DESCRIPTION FILES from FIRST R Package Release Folders

```{r, eval = FALSE}
#Parallel Analysis
plan(multisession, workers = parallel::detectCores() - 1)
n <- length(pkg_name_vec)
results.desc <- lapply(1:n, function(i) {
  future({
    
    ## Name Pkg
    name_i <- pkg_name_vec[i]
    
    ## Get Description FILE
    desc.i<-read_lines(paste0("/Users/antiporta/Downloads/pkg_untar/", 
                              pkg_name_vec[i], 
                              "/DESCRIPTION"))
    
    ## Store results for this particular package name
    list(name_i, desc.i)
  })
})

## Wrap up the results
results <- lapply(results.desc, value)
desc.files.pkg <-  sapply(results,`[`,2)
saveRDS(desc.files.pkg, 
  file = paste0(project.dir, "Rmd_files/2018-11-25-feature_task_part2/desc_files_RDS")
```

## Working in KEY features
```{r}
desc.files.pkg<-readRDS(paste0(project.dir, "Rmd_files/2018-11-25-feature_task_part2/desc_files_RDS"))
```

###TITLE

```{r}
list.pkg_title<-vector(mode="list", length=length(pkg_name_vec))
names(list.pkg_title) <- pkg_name_vec
for (i in 1:length(pkg_name_vec)) {
  pkg.title.i<-grep("^Title", desc.files.pkg[[i]])
  pkg.title.i<-desc.files.pkg[[i]][pkg.title.i]
  pkg.title.i<-gsub(".*:", "", pkg.title.i) 
  pkg.title.i<-trimws(pkg.title.i)
  list.pkg_title[[i]]<-pkg.title.i
}
pkg_title.df <- do.call(rbind, list.pkg_title)
pkg_title.df <- cbind.data.frame(pkg_name_vec, pkg_title.df)

## Save data frame with pkg_name, first_release
out.path <- file.path(project.dir, "data/pkg_first_release_title.csv")
write.csv(pkg_title.df , 
          out.path, row.names = TRUE, quote = TRUE)
```

###PACKAGE VERSION

```{r}
list.pkg.version<-vector(mode="list", length=length(pkg_name_vec))
names(list.pkg.version) <- pkg_name_vec
for (i in 1:length(pkg_name_vec)) {
  pkg.version.i<-grep("^Version", desc.files.pkg[[i]])
  pkg.version.i<-desc.files.pkg[[i]][pkg.version.i]
  pkg.version.i<-gsub(".*:", "", pkg.version.i) 
  pkg.version.i<-trimws(pkg.version.i)
  list.pkg.version[[i]]<-pkg.version.i
}
pkg.version.df <- do.call(rbind, list.pkg.version)
length(unique(pkg.version.df))
table(pkg.version.df)

#Package Versions (Binary)
pkg_ver<-pkg.version.df
pkg_ver<-sapply(str_split(pkg_ver, "\\."), "[", 1)
pkg_ver<-replace(pkg_ver, pkg_ver=="1-00", 1)
pkg_ver<-replace(pkg_ver, pkg_ver=="2017", 0)
pkg_ver<-replace(pkg_ver, pkg_ver!="0", 1)
pkg_ver<-as.numeric(pkg_ver)
```

###LICENSE

```{r}
list.pkg.license<-vector(mode="list", length=length(pkg_name_vec))
names(list.pkg.license) <- pkg_name_vec
for (i in 1:length(pkg_name_vec)) {
  pkg.license.i<-grep("^License\\:", desc.files.pkg[[i]])
  pkg.license.i<-desc.files.pkg[[i]][pkg.license.i]
  pkg.license.i<-gsub(".*:", "", pkg.license.i) 
  pkg.license.i<-trimws(pkg.license.i)
  list.pkg.license[[i]]<-pkg.license.i
}
pkg.license.df <- do.call(rbind, list.pkg.license)
summary(pkg.license.df, maxsum=20)
anyNA(pkg.license.df)
#License (grouping)
license_group<-pkg.license.df
  license_group[which(grepl("^GPL", license_group))]<-
  "GPL"
  license_group[which(grepl("^GNU", license_group))]<-"GPL"
  license_group[which(grepl("^Apache", license_group))]<-"Apache"
  license_group[which(grepl("^AGPL", license_group))]<-"AGPL"
  license_group[which(grepl("^Mozilla", license_group))]<-"MPL"
  license_group[which(grepl("^MPL", license_group))]<-"MPL"
  license_group[which(grepl("^LGPL", license_group))]<-"LGPL"
  license_group[which(grepl("^BSD", license_group))]<-"BSD"
  license_group[which(grepl("^MIT", license_group))]<-"MIT"
  license_group[which(grepl("^FreeBSD", license_group))]<-"FreeBSD"
  license_group[which(grepl("^CC BY", license_group))]<-"CC BY"
  license_group[which(grepl("^Boost", license_group))]<-"BSL"
  license_group[which(grepl("^BSL", license_group))]<-"BSL"
table(license_group)
license_group <- license_group%>% as.data.frame() %>% 
  group_by(V1) %>% mutate(count=n())
saveRDS(license_group, 
  file = paste0(project.dir,
                "/Rmd_files/2018-11-25-feature_task_part2/license_group"))

#rownames_to_column(license_group, var = "pkg")
```

###ROXYGEN USE

```{r}
list.pkg.roxygen<-vector(mode="list", length=length(pkg_name_vec))
names(list.pkg.roxygen) <- pkg_name_vec
for (i in 1:length(pkg_name_vec)) {
  pkg.roxygen.i<-grep("^Roxygen", desc.files.pkg[[i]])
  if (length(pkg.roxygen.i)!=0){
    pkg.roxygen.i<-desc.files.pkg[[i]][pkg.roxygen.i]
    pkg.roxygen.i<-gsub(".*:", "", pkg.roxygen.i) 
    pkg.roxygen.i<-trimws(pkg.roxygen.i)
  } else{
    pkg.roxygen.i<-NA
  }
  list.pkg.roxygen[[i]]<-pkg.roxygen.i
}
pkg.roxygen.df <- do.call(rbind, list.pkg.roxygen)
table(pkg.roxygen.df)
#Roxygen (Y/N)
roxygen_yn<- replace(pkg.roxygen.df, pkg.roxygen.df!="", 1)
roxygen_yn<- replace(roxygen_yn, is.na(roxygen_yn), 0)
```

###DEPENDS/IMPORTS/SUGGESTS/LINKING TO

```{r, eval=FALSE}
library(desc)
plan(multisession, workers = parallel::detectCores() - 1)
n <- length(pkg_name_vec)
results.deps <- lapply(1:n, function(i) {
  future({
    ## Name Pkg
    name_i <- pkg_name_vec[i]
    ## Get Imports/Depends/etc
    out.path.pkg <- file.path("/Users/antiporta/Downloads/pkg_untar/",
      name_i, "DESCRIPTION")
    deps.i<-desc::desc_get_deps(out.path.pkg)
    ## Store results for this particular package name
    list(name_i, deps.i)
  })
})
## Wrap up the results
results.deps.d <- lapply(results.deps, value)
deps.files.pkg <-  sapply(results.deps.d,`[`,2)
saveRDS(deps.files.pkg, 
  file = "/Users/antiporta/Dropbox/712-final_project/Rmd_files/2018-11-25-feature_task_part2/deps_pkg_RDS")
```

```{r}
## Number of Depends/Suggests/etc
deps.files.pkg<-readRDS(paste0(project.dir,"Rmd_files/2018-11-25-feature_task_part2/deps_pkg_RDS"))
list.pkg.deps<-vector(mode="list", length=length(pkg_name_vec))
names(list.pkg.deps) <- pkg_name_vec
for (i in 1:length(pkg_name_vec)){
  data.i<-as.data.frame(deps.files.pkg[i])
  rpos<- grep("\\bR$", data.i$package)
  if (length(rpos)==0){
    rpos<-which(grepl("^R\\.", data.i$package))
    vpos<-which(grepl("*", data.i$version))
    rpos<-which(rpos==vpos)
  } 
  if (length(rpos)!=0){
    data.i<- data.i %>% filter(row_number()!=rpos) %>%
     summarize(n=n()) %>% as.numeric()
  } else{
    data.i<- data.i  %>% summarize(n=n()) %>% as.numeric()
  }
  list.pkg.deps[[i]]<-data.i 
} 
pkg.depends.df <- do.call(rbind,list.pkg.deps)
table(pkg.depends.df)
anyNA(pkg.depends.df)
```

###MINIMUN R VERSION COMPATIBLE

```{r}
list.pkg.rversion<-vector(mode="list", length=length(pkg_name_vec))
names(list.pkg.rversion) <- pkg_name_vec
for (i in 1:length(pkg_name_vec)){
  rversion.i<-as.data.frame(deps.files.pkg[i])
  rpos<- grep("\\bR$", rversion.i$package)
  if (length(rpos)==0){
    rpos<-which(grepl("^R\\.", rversion.i$package))
    vpos<-which(grepl("*", rversion.i$version))
    rpos<-which(rpos==vpos)
  } 
  if (length(rpos)!=0){
    rversion.i<- rversion.i %>% filter(row_number()==rpos) %>%
     select(version) %>% as.character()
  } else{
    rversion.i<- NA
  }
  list.pkg.rversion[[i]]<-rversion.i 
} 
pkg.rversion.df <- do.call(rbind,list.pkg.rversion)
table(pkg.rversion.df)
#R Master releases
#install.packages("rversions")
library(rversions)
master.rversions<-r_versions()
master.rversions<-master.rversions[which(grepl("2.0.0",master.rversions$version)):110,]
master.rversions$date<-as.Date(master.rversions$date)
unique(master.rversions$version)
#Clean R-version Variable
library(stringr)
length(pkg.rversion.df)
rver.p1<-substr(pkg.rversion.df, start = 1, stop = 2)
rver.p1<-trimws(rver.p1)
rver.p2<-substr(pkg.rversion.df, start = 3, stop = 100)
rver.p2[which(grepl("^\\\n",rver.p2))]<-
  "3.0.0"
rver.p2<-trimws(rver.p2)
#rver.p2[which(rver.p2=="3.00")]<-
#  "3.0.0"
length(unique(rver.p2))
rver.p2<-replace(rver.p2, rver.p2=="", NA)
length(unique(rver.p2))
rver.p3<-str_split_fixed(rver.p2, "\\.", n=3 )
rver1<-sapply(rver.p3[,1],`[`,1)
rver2<-sapply(rver.p3[,2],`[`,1)
rver3<-sapply(rver.p3[,3],`[`,1)
rver3[rver1!=""]<-"0"
clean.rver<-paste(as.numeric(rver1), as.numeric(rver2), as.numeric(rver3), sep=".")
clean.rver[clean.rver=="NA.NA.NA"]<-NA
unique(clean.rver)
which(!(clean.rver[!is.na(clean.rver)] %in% unique(master.rversions$version)))
clean.rver[!is.na(clean.rver)][604] #This R version DOES NOT exist! change to next one available
#Match with master and put minimum R required version
length(clean.rver[!is.na(clean.rver) & clean.rver!="2.16.0"])
clean.rver[clean.rver=="2.16.0"]<-"3.0.0" #This R version DOES NOT exist! change to next one available
##Change values when the sign is >
norder<-match(clean.rver[which(rver.p1==">")], master.rversions$version)
clean.rver[which(rver.p1==">")]<-master.rversions$version[norder+1]
unique(clean.rver)
##Dealing with the NA, link with pkg release date.
first_release_dates<-read_csv(paste0(project.dir,
                                     "data/pkg_first_release_SUBSET.csv"))
first_release_dates<-first_release_dates %>%
  select(pkg_name, first_release)
##Get closest date AFTER launch
closest_after_date<-vector(mode="list", length=length(pkg_name_vec))
for (i in 1:length(closest_after_date)){
  closest_after_date[i]<-
    master.rversions$date[master.rversions$date>first_release_dates$first_release[i]][1]
}
closest_after_date <- do.call(rbind,closest_after_date)
closest_after_date <- as.Date(closest_after_date, origin = "1970-01-01")
clean.rver1<-
  master.rversions$version[match(closest_after_date, master.rversions$date)]
clean.rver_modified<-ifelse(is.na(clean.rver), clean.rver1, clean.rver)
##Calculating numeric value for R version
clean.rver_part<-str_split_fixed(clean.rver, "\\.", n=3 )
rver1<-sapply(clean.rver_part[,1],`[`,1)
rver2<-sapply(clean.rver_part[,2],`[`,1)
rver3<-sapply(clean.rver_part[,3],`[`,1)
unique(clean.rver)
unique(rver1)
unique(rver2)
unique(rver3)
rversion_final<-as.numeric(rver1)*100
rversion_final<-rversion_final+as.numeric(rver2)
rversion_final<-rversion_final+(as.numeric(rver3)*.1)
rversion_final<-as.numeric(rversion_final)
unique(rversion_final)
##Calculating numeric value for R version MODIFIED (NAs)
clean.rver_part_m<-str_split_fixed(clean.rver_modified, "\\.", n=3 )
rver1_m<-sapply(clean.rver_part_m[,1],`[`,1)
rver2_m<-sapply(clean.rver_part_m[,2],`[`,1)
rver3_m<-sapply(clean.rver_part_m[,3],`[`,1)
unique(clean.rver_modified)
unique(rver1_m)
unique(rver2_m)
unique(rver3_m)
rversion_final_m<-as.numeric(rver1_m)*100
rversion_final_m<-rversion_final_m+as.numeric(rver2_m)
rversion_final_m<-rversion_final_m+(as.numeric(rver3_m)*.1)
rversion_final_m<-as.numeric(rversion_final_m)
unique(rversion_final_m)
```

###AUTHORS

```{r}
authors.df<-tools::CRAN_package_db()
authors.df <- authors.df[, c(1,17)]
#authors.df<-authors.df[authors.df$Package %in% pkg_name_vec,]
authors.df<-left_join(first_release_dates,authors.df, by=c("pkg_name"="Package")) %>% select(-first_release)
authors.vec<-gsub("\\(.*?\\)", "", authors.df$Author)
authors.vec<-gsub("\\[.*?\\]", "", authors.vec) 
authors.vec<-str_replace(authors.df$Author, "\\[.*\\]", "")
n_authors<-str_count(authors.vec, ",")
n_authors<-n_authors+1
#which(n_authors==35)
#which(is.na(n_authors))
n_authors[889]<-1
n_authors[1572]<-2
table(n_authors)
authors.df_final<-cbind.data.frame(pkg_name_vec, n_authors)
authors.df_final$pkg_name_vec<-as.character(authors.df_final$pkg_name_vec)
saveRDS(authors.df_final, 
  file = paste0(project.dir,
                "/Rmd_files/2018-11-25-feature_task_part2/authors.df_final"))
```


###CREATE DATA FILE

```{r, eval=FALSE}
length(n_authors)
features.pkg<-cbind.data.frame(pkg_name_vec,
                    pkg_ver,
                    license_group,
                    roxygen_yn,
                    pkg.depends.df,
                    rversion_final,
                    rversion_final_m,
                    n_authors)
names(features.pkg)<-
  c("pkg_name", "pkg_version", 
    "license_group", "roxygen_yn", 
    "n_depends","rversion_min",
    "rversion_min_modified", "nauthors")
features.pkg$pkg_name<-as.character(features.pkg$pkg_name)
  
## Save data frame with pkg_name, first_release
saveRDS(features.pkg, 
  file = paste0(project.dir,
    "Rmd_files/2018-11-25-feature_task_part2/df_deps_pkgs_final"))
out.path <- file.path(project.dir, "data/feature_task/features_extracted_part2.csv")
write.csv(features.pkg, 
          out.path, 
          row.names = FALSE,
          quote = TRUE)
```



