---
title: 'Features engineering: other features from code'
author: "Marta Karas"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: false
    toc_depth: 3
---

- vignette: pages (min / max / mean)
- reference manual: number of functions exported
- reference manual: unique number of papers cited


```{r, include = FALSE}
rm(list = ls())
knitr::opts_chunk$set(include = TRUE, comment = NA, cache = FALSE, 
                      message = FALSE, warning = FALSE)
options(stringsAsFactors=FALSE)

```

* Define project folder `712-final_project` path. That is, modify `project.dir` string below; once it points to your `712-final_project` folder location, all other stuff below would work. 

```{r}

library(rvest)
library(ggplot2)
library(dplyr)
library(future)
library(stringi)
library(tm)
library(tools)

user.name<-Sys.info()[7]
if(user.name=="antiporta") project.dir <- "/Users/antiporta/Dropbox/712-final_project/"
if(user.name=="mkaras") project.dir <- "/Users/mkaras/Dropbox/JHU/711-ADV_DATA_SCIENCE/712-final_project"
```


# Read `data.frame` with package name, package first release 

```{r}
path.tmp <- file.path(project.dir, "data/pkg_first_release_SUBSET.csv")
pkg_first_rel <- read.csv(path.tmp, stringsAsFactors = FALSE)
pkg_first_rel$first_release <- as.Date(pkg_first_rel$first_release)

## Preview
head(pkg_first_rel)
packageNames.vec <- pkg_first_rel$pkg_name

pkg_install_dir <- "/Users/mkaras/Documents/JHU/712-final_project_MY_WORKSPACE/data/pkg_installation_dir/"

```



# 1. has tests? 

```{r, eval = FALSE}

testthat.present.vec <- numeric()
testthat.files.lines.cnt.vec <- numeric()

n <- length(packageNames.vec)

for (i in 1:n){
  
  pkg_name.i <- packageNames.vec[i]
  pkg_dir.i <- paste0(pkg_install_dir, pkg_name.i)
  all.contained.dirs <- list.dirs(pkg_dir.i, full.names = FALSE, recursive = FALSE)
  all.contained.dirs <- all.contained.dirs[nchar(all.contained.dirs) > 0]
  
  ## Set counters for current package
  testthat.present <- 0
  testthat.files.lines.cnt <- 0
  
  ## Check if has tests dir
  if ("tests" %in% all.contained.dirs){
    tests.dir.i <- paste0(pkg_install_dir, pkg_name.i, "/tests")
    tests.contained.dirs <-  list.dirs(tests.dir.i, full.names = FALSE, recursive = FALSE)
    
    ## Check if has tests/testthat dir 
    if ( (length(tests.contained.dirs) > 0) & ("testthat" %in% tests.contained.dirs)){
      testthat.present <- 1
      testthat.dir.i <- paste0(pkg_install_dir, pkg_name.i, "/tests/testthat")
      testthat.files <- list.files(testthat.dir.i, full.names = TRUE)
      
      ## Count number of non-empty lines within tests/testthat R files
      for (testthat.file.tmp in testthat.files){
        if (!(file_ext(testthat.file.tmp) == "R")) next
        readtext.out <- readLines(testthat.file.tmp)
        readtext.out.empty_lines <- grepl('^\\s*$', readtext.out)
        readtext.out <- readtext.out[!readtext.out.empty_lines]
        ## Increment counter by number of non-empty lines identified
        testthat.files.lines.cnt <- testthat.files.lines.cnt + length(readtext.out)
      }
    }
  }
  
  ## Save results for current package
  testthat.present.vec <- c(testthat.present.vec, testthat.present)
  testthat.files.lines.cnt.vec <- c(testthat.files.lines.cnt.vec, testthat.files.lines.cnt)

}

out_df <- data.frame(
  pkg_name = packageNames.vec,
  testthat_dir_present = testthat.present.vec,
  testthat_R_files_lines_cnt = testthat.files.lines.cnt.vec)

out_df %>% filter(testthat_dir_present == 1) %>% arrange(testthat_R_files_lines_cnt)
out_df %>% filter(testthat_dir_present == 1) %>% arrange(desc(testthat_R_files_lines_cnt))

table(out_df$testthat_dir_present)

# out.path <- file.path(project.dir, "data/testthat_files.csv")
# write.csv(out_df, out.path, row.names = FALSE, quote = FALSE)
```


# 2. has demo? 

```{r, eval = FALSE}

pkg_install_dir <- "/Users/mkaras/Documents/JHU/712-final_project_MY_WORKSPACE/data/pkg_installation_dir/"

demo.present.vec <- numeric()
demo.files.lines.cnt.vec <- numeric()

n <- length(packageNames.vec)

for (i in 1:n){
  
  pkg_name.i <- packageNames.vec[i]
  pkg_dir.i <- paste0(pkg_install_dir, pkg_name.i)
  all.contained.dirs <- list.dirs(pkg_dir.i, full.names = FALSE, recursive = FALSE)
  all.contained.dirs <- all.contained.dirs[nchar(all.contained.dirs) > 0]
  
  ## Set counters for current package
  demo.present <- 0
  demo.files.lines.cnt <- 0
  
  ## Check if has tests dir
  if ("demo" %in% all.contained.dirs){
    demo.present <- 1
    demo.dir.i <- paste0(pkg_install_dir, pkg_name.i, "/demo")
    demo.contained.dirs <-  list.files(demo.dir.i, full.names = TRUE, recursive = TRUE)

    ## Check if has tests/demo dir
    for (demo.file.tmp in demo.contained.dirs){
      if (!(file_ext(demo.file.tmp) == "R")) next
      readtext.out <- readLines(demo.file.tmp)
      readtext.out.empty_lines <- grepl('^\\s*$', readtext.out)
      readtext.out <- readtext.out[!readtext.out.empty_lines]
      ## Increment counter by number of non-empty lines identified
      demo.files.lines.cnt <- demo.files.lines.cnt + length(readtext.out)
    }
  }

  ## Save results for current package
  demo.present.vec <- c(demo.present.vec, demo.present)
  demo.files.lines.cnt.vec <- c(demo.files.lines.cnt.vec, demo.files.lines.cnt)

}

out_df <- data.frame(
  pkg_name = packageNames.vec,
  demo_dir_present = demo.present.vec,
  demo_R_files_lines_cnt = demo.files.lines.cnt.vec)

out_df %>% filter(demo_dir_present == 1) %>% arrange(demo_R_files_lines_cnt)
out_df %>% filter(demo_dir_present == 1) %>% arrange(desc(demo_R_files_lines_cnt))


table(out_df$demo_dir_present)

# out.path <- file.path(project.dir, "data/demo_files.csv")
# write.csv(out_df, out.path, row.names = FALSE, quote = FALSE)
```



# 3. data included in the package? 

```{r, eval = FALSE}

pkg_install_dir <- "/Users/mkaras/Documents/JHU/712-final_project_MY_WORKSPACE/data/pkg_installation_dir/"

data_dir_present.vec <- numeric()

data_size_total.vec <- numeric()
data_size_rda.vec   <- numeric()
data_size_RData.vec <- numeric()
data_size_txt.vec   <- numeric()
data_size_gz.vec    <- numeric()
data_size_csv.vec   <- numeric()

data_cnt_total.vec <- numeric()
data_cnt_rda.vec   <- numeric()
data_cnt_RData.vec <- numeric()
data_cnt_txt.vec   <- numeric()
data_cnt_gz.vec    <- numeric()
data_cnt_csv.vec   <- numeric()

n <- length(packageNames.vec)

all.ext <- numeric()

for (i in 1:n){
  
  pkg_name.i <- packageNames.vec[i]
  pkg_dir.i <- paste0(pkg_install_dir, pkg_name.i)
  all.contained.dirs <- list.dirs(pkg_dir.i, full.names = FALSE, recursive = FALSE)
  all.contained.dirs <- all.contained.dirs[nchar(all.contained.dirs) > 0]
  
  ## Set counters for current package
  data_dir_present.tmp <- 0
  
  data_size_total.tmp <- 0
  data_size_rda.tmp   <- 0
  data_size_RData.tmp <- 0
  data_size_txt.tmp   <- 0
  data_size_gz.tmp    <- 0
  data_size_csv.tmp   <- 0
  
  data_cnt_total.tmp <- 0
  data_cnt_rda.tmp   <- 0
  data_cnt_RData.tmp <- 0
  data_cnt_txt.tmp   <- 0
  data_cnt_gz.tmp    <- 0
  data_cnt_csv.tmp   <- 0
    
  ## Check if has tests dir
  if ("data" %in% all.contained.dirs){
    data_dir_present.tmp <- 1
    data.dir.i <- paste0(pkg_install_dir, pkg_name.i, "/data")
    data.contained.dirs <-  list.files(data.dir.i, full.names = TRUE, recursive = TRUE)
    all.ext <- c(all.ext, sapply(data.contained.dirs, function(i) file_ext(i)))
    
    # Check size of data 
    for (data.file.tmp in data.contained.dirs){
      file.s <- file.size(data.file.tmp)
      file.ext <- file_ext(data.file.tmp)
      
      data_size_total.tmp <- data_size_total.tmp + file.s
      if (file.ext == "rda") data_size_rda.tmp <- data_size_rda.tmp + file.s
      if (file.ext %in% c("RData", "rdata", "Rdata")) data_size_RData.tmp <- data_size_RData.tmp + file.s
      if (file.ext == "txt") data_size_txt.tmp <- data_size_txt.tmp + file.s
      if (file.ext == "gz") data_size_gz.tmp <- data_size_gz.tmp + file.s
      if (file.ext == "csv") data_size_csv.tmp <- data_size_csv.tmp + file.s
      
      data_cnt_total.tmp <- data_cnt_total.tmp + 1
      if (file.ext == "rda") data_cnt_rda.tmp <- data_cnt_rda.tmp + 1
      if (file.ext %in% c("RData", "rdata", "Rdata")) data_cnt_RData.tmp <- data_cnt_RData.tmp + 1
      if (file.ext == "txt") data_cnt_txt.tmp <- data_cnt_txt.tmp + 1
      if (file.ext == "gz") data_cnt_gz.tmp <- data_cnt_gz.tmp + 1
      if (file.ext == "csv") data_cnt_csv.tmp <- data_cnt_csv.tmp + 1
    }
  }

  ## Save results for current package
  data_dir_present.vec <- c(data_dir_present.vec, data_dir_present.tmp)
  
  data_size_total.vec  <- c(data_size_total.vec, data_size_total.tmp)
  data_size_rda.vec    <- c(data_size_rda.vec, data_size_rda.tmp)
  data_size_RData.vec  <- c(data_size_RData.vec, data_size_RData.tmp)
  data_size_txt.vec    <- c(data_size_txt.vec, data_size_txt.tmp)
  data_size_gz.vec     <- c(data_size_gz.vec, data_size_gz.tmp)
  data_size_csv.vec    <- c(data_size_csv.vec, data_size_csv.tmp)
  
  data_cnt_total.vec  <- c(data_cnt_total.vec, data_cnt_total.tmp)
  data_cnt_rda.vec    <- c(data_cnt_rda.vec, data_cnt_rda.tmp)
  data_cnt_RData.vec  <- c(data_cnt_RData.vec, data_cnt_RData.tmp)
  data_cnt_txt.vec    <- c(data_cnt_txt.vec, data_cnt_txt.tmp)
  data_cnt_gz.vec     <- c(data_cnt_gz.vec, data_cnt_gz.tmp)
  data_cnt_csv.vec    <- c(data_cnt_csv.vec, data_cnt_csv.tmp)
}

sort(table(all.ext))


out_df <- data.frame(
  pkg_name = packageNames.vec,
  data_dir_present = data_dir_present.vec,
  
  data_size_total = data_size_total.vec,
  data_size_rda = data_size_rda.vec,
  data_size_rdata = data_size_RData.vec,
  data_size_txt = data_size_txt.vec,
  data_size_gz = data_size_gz.vec,
  data_size_csv = data_size_csv.vec,
  
  data_cnt_total = data_cnt_total.vec,
  data_cnt_rda = data_cnt_rda.vec,
  data_cnt_rdata = data_cnt_RData.vec,
  data_cnt_txt = data_cnt_txt.vec,
  data_cnt_gz = data_cnt_gz.vec,
  data_cnt_csv = data_cnt_csv.vec)

## stats
out_df %>% select(-pkg_name) %>% summarise_all(sum)
table(out_df$data_dir_present)

# out.path <- file.path(project.dir, "data/data_folder_files.csv")
# write.csv(out_df, out.path, row.names = FALSE, quote = FALSE)
```



# 4. src folder included in the package? 

```{r, eval = FALSE}

pkg_install_dir <- "/Users/mkaras/Documents/JHU/712-final_project_MY_WORKSPACE/data/pkg_installation_dir/"

src_dir_present.vec <- numeric()

src_size_total.vec <- numeric()
src_size_h.vec     <- numeric()
src_size_cpp.vec   <- numeric()
src_size_c.vec     <- numeric()

src_cnt_total.vec  <- numeric()
src_cnt_h.vec      <- numeric()
src_cnt_cpp.vec    <- numeric()
src_cnt_c.vec      <- numeric()


n <- length(packageNames.vec)

all.ext <- numeric()

for (i in 1:n){
  
  pkg_name.i <- packageNames.vec[i]
  pkg_dir.i <- paste0(pkg_install_dir, pkg_name.i)
  all.contained.dirs <- list.dirs(pkg_dir.i, full.names = FALSE, recursive = FALSE)
  all.contained.dirs <- all.contained.dirs[nchar(all.contained.dirs) > 0]
  
  ## Set counters for current package
    src_dir_present.tmp <- 0
    
    src_size_total.tmp  <- 0
    src_size_h.tmp      <- 0
    src_size_cpp.tmp    <- 0
    src_size_c.tmp      <- 0
    
    src_cnt_total.tmp  <- 0
    src_cnt_h.tmp      <- 0
    src_cnt_cpp.tmp    <- 0
    src_cnt_c.tmp      <- 0

  ## Check if has tests dir
  if ("src" %in% all.contained.dirs){
    src_dir_present.tmp <- 1
    src.dir.i <- paste0(pkg_install_dir, pkg_name.i, "/src")
    src.contained.files <-  list.files(src.dir.i, full.names = TRUE, recursive = TRUE)

    all.ext <- c(all.ext, sapply(src.contained.files, function(i) file_ext(i)))
    # Check size of data
    for (src.file.tmp in src.contained.files){
      file.s <- file.size(src.file.tmp)
      file.ext <- file_ext(src.file.tmp)
      
      src_size_total.tmp <- src_size_total.tmp + file.s
      if (file.ext == "h") src_size_h.tmp <- src_size_h.tmp + file.s
      if (file.ext == "cpp") src_size_cpp.tmp <- src_size_cpp.tmp + file.s
      if (file.ext == "c") src_size_c.tmp <- src_size_c.tmp + file.s
      
      src_cnt_total.tmp <- src_cnt_total.tmp + 1
      if (file.ext == "h") src_cnt_h.tmp <- src_cnt_h.tmp + 1
      if (file.ext == "cpp") src_cnt_cpp.tmp <- src_cnt_cpp.tmp + 1
      if (file.ext == "c") src_cnt_c.tmp <- src_cnt_c.tmp + 1
    }
  }

  ## Save results for current package
  src_dir_present.vec <- c(src_dir_present.vec, src_dir_present.tmp)
  
  src_size_total.vec  <- c(src_size_total.vec, src_size_total.tmp)
  src_size_h.vec      <- c(src_size_h.vec, src_size_h.tmp)
  src_size_cpp.vec    <- c(src_size_cpp.vec, src_size_cpp.tmp)
  src_size_c.vec      <- c(src_size_c.vec, src_size_c.tmp)
  
  src_cnt_total.vec  <- c(src_cnt_total.vec, src_cnt_total.tmp)
  src_cnt_h.vec      <- c(src_cnt_h.vec, src_cnt_h.tmp)
  src_cnt_cpp.vec    <- c(src_cnt_cpp.vec, src_cnt_cpp.tmp)
  src_cnt_c.vec      <- c(src_cnt_c.vec, src_cnt_c.tmp)

}

sort(table(all.ext))

out_df <- data.frame(
  pkg_name = packageNames.vec,
  src_dir_present = src_dir_present.vec,
  
  src_files_size_total = src_size_total.vec,
  src_files_size_h = src_size_h.vec,
  src_files_size_cpp = src_size_cpp.vec,
  src_files_size_c = src_size_c.vec,
  
  src_files_cnt_total = src_cnt_total.vec,
  src_files_cnt_h = src_cnt_h.vec,
  src_files_cnt_cpp = src_cnt_cpp.vec,
  src_files_cnt_c = src_cnt_c.vec)

## stats
out_df %>% select(-pkg_name) %>% summarise_all(sum)
table(out_df$src_dir_present)


# out.path <- file.path(project.dir, "data/src_folder_files.csv")
# write.csv(out_df, out.path, row.names = FALSE, quote = FALSE)
```




# Produce final data frame 

```{r}

## Read and merge them alls
out.path <- file.path(project.dir, "data/testthat_files.csv")
testthat_files <- read.csv(out.path, stringsAsFactors = FALSE)

out.path <- file.path(project.dir, "data/demo_files.csv")
demo_files <- read.csv(out.path, stringsAsFactors = FALSE)

out.path <- file.path(project.dir, "data/data_folder_files.csv")
data_folder_files <- read.csv(out.path, stringsAsFactors = FALSE)

out.path <- file.path(project.dir, "data/src_folder_files.csv")
src_folder_files <- read.csv(out.path, stringsAsFactors = FALSE)

df_final <- 
  testthat_files %>%
  left_join(demo_files, by = "pkg_name")  %>%
  left_join(data_folder_files, by = "pkg_name") %>%
  left_join(src_folder_files, by = "pkg_name")

## Sanity check
head(df_final)
dim(testthat_files)
dim(df_final)
any(is.na(df_final))
df_final %>% select(-pkg_name) %>% summarise_all(sum)


## Interesting stats
round(mean(df_final$testthat_dir_present),3)
round(mean(df_final$demo_dir_present),3)
round(mean(df_final$data_dir_present),3)
round(mean(df_final$src_dir_present),3)


out.path <- file.path(project.dir, "data/feature_task/features_extracted_part4_pkg_code.csv")
write.csv(df_final, out.path, row.names = FALSE, quote = FALSE)

```











