---
title: 'Modeling: linear regression'
author: 
- "Marta Karas"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: false
    toc_depth: 3
---


```{r, include = FALSE}
rm(list = ls())
knitr::opts_chunk$set(include = TRUE, comment = NA, cache = TRUE, 
                      message = FALSE, warning = FALSE)

```

* Define project folder `712-final_project` path. That is, modify `project.dir` string below; once it points to your `712-final_project` folder location, all other stuff below would work. 

```{r}
user.name <- Sys.info()[7]
if(user.name=="antiporta") project.dir <- "/Users/antiporta/Dropbox/712-final_project/"
if(user.name=="mkaras") project.dir <- "/Users/mkaras/Dropbox/JHU/711-ADV_DATA_SCIENCE/712-final_project/"

library(caret)
library(dplyr)
library(reshape2)
library(ggplot2)
library(fastDummies)
library(janitor)
```


# Read data 

```{r}

out.path <- file.path(project.dir, "data/final_dfs/data_x.csv")
x_df0 <- read.csv(out.path, stringsAsFactors = FALSE)
# head(x_df0)

out.path <- file.path(project.dir, "data/final_dfs/data_y.csv")
y_df0 <- read.csv(out.path, stringsAsFactors = FALSE)
# head(y_df0)

```

# Mutate data 

### Create subset of columns of `x` data which will be used in modelling

```{r}
# apply(x_df0, 2, function(col) any(is.na(col)))
x_df0 <- 
  x_df0 %>% 
  select(-pkg_name,
         -rversion_min)

names(x_df0)[apply(x_df0, 2, function(col) any(is.na(col)))]
x_df0[is.na(x_df0)] <- 0
names(x_df0)[apply(x_df0, 2, function(col) any(is.na(col)))]
x_df <- x_df0
```


### Create dummy variables for subset of columns of `x`

```{r}
## x_df_license_group
x_df_license_group <- x_df %>% select(license_group)
x_df_license_group_DUMMY <- 
  dummy_cols(x_df_license_group,
             remove_most_frequent_dummy = TRUE) %>%
  select(-license_group)
x_df_license_group_DUMMY <- as.data.frame(clean_names(x_df_license_group_DUMMY))
x_df <- cbind(x_df %>% select(-license_group),
              x_df_license_group_DUMMY)
# x_df <- scale(x_df, center = TRUE, scale = TRUE)
x_df <- as.data.frame(x_df)

## Sanity check
table(sapply(x_df, class))

```

### Mutate columns of `y` 

```{r}
y_df <- 
  y_df0 %>%
  select(-pkg_name) %>%
  mutate(download_cnt_90d_LOG = log(download_cnt_90d),
         download_cnt_365d_LOG = log(download_cnt_365d))
# y_df <- scale(y_df, center = TRUE, scale = TRUE)
y_df <- as.data.frame(y_df)

```


# Package documentation and vignette explored

- any vignette

```{r EDA_vignette_cnt, fig.width=8, fig.height=4}

data_df <- cbind(y_df, x_df)
gg.base_size <- 12

round(mean(data_df$vignette_any) * 100, 2)

data_df$var <- factor(as.character(data_df$vignette_any), 
                      levels = c(1,0),
                      labels = c("Yes", "No"))

tbl <- table((data_df  %>% filter(vignette_any == 1))$vignette_cnt)
tbl / sum(tbl)

ggplot(data = data_df  %>% filter(vignette_any == 1), 
       aes(x = vignette_cnt)) +
  scale_fill_manual(values = c("green", "grey")) + 
  geom_bar(color = "black", alpha = 0.6) + 
  theme_bw(base_size = gg.base_size) + 
  labs(title = "Barplot of packages count\n(limited to packages with at least one vignette)",
       x = "# of vignettes per package",
       y = "packages count") + 
  theme(legend.position = "none") + 
  scale_x_continuous(breaks = 1:max(data_df$vignette_cnt))

```


- any vignette vs log number of downloads 

```{r EDA_vignette_cnt_vs_downloads, fig.width=5.5, fig.height=4}


data_df$vars <- factor(as.character(data_df$vignette_any), 
                      levels = c(1,0),
                      labels = c("Yes", "No"))

ggplot(data_df,
       aes(x = vars, 
           y = download_cnt_365d_LOG,
           group = vars,
           fill = vars)) +
  scale_fill_manual(values = c("green", "grey")) + 
  geom_boxplot(color = "black", alpha = 0.6) + 
  theme_bw(base_size = gg.base_size) + 
  labs(title = "Boxplot of log(# of downloads over 1y) of packages\nstratified by whether or not\na package has a vignette",
       x = "Has any vignette?",
       y = "log(# of downloads over 1y)") + 
  theme(legend.position = "none") 

```


- vignette_words_cnt_median

```{r EDA_vignette_words_cnt_median, fig.width=6, fig.height=5}


summary((data_df  %>% filter(vignette_any == 1))$vignette_words_cnt_median)

ggplot(data = data_df  %>% filter(vignette_any == 1), 
       aes(x = "", 
           y = vignette_words_cnt_median)) +
  geom_boxplot(color = "black", alpha = 0.6) + 
  theme_grey(base_size = gg.base_size) + 
  labs(title = "Boxplot of number of words (>= 3 letters) in vignette\n(median value across all vignettes,\nif package has >1 vignette))",
       x = "",
       y = "number of words (>= 3 letters) in vignette") + 
  theme(legend.position = "none") 

```


# Code features explored

```{r EDA_directory_present, fig.width=6, fig.height=4}

gg.base_size <- 12

data_df.agg <- 
  data_df %>%
  select(testthat_dir_present,
         demo_dir_present,
         src_dir_present) %>%
  summarise_all(mean)
data_df.agg.m <- 
  melt(data_df.agg) %>%
  arrange(value)
data_df.agg.m$variable <- 
  factor(as.character(data_df.agg.m$variable),
         levels = c("demo_dir_present", "src_dir_present", "testthat_dir_present"),
         labels = c("demo directory present", "src directory present", "testthat directory present"))


ggplot(data_df.agg.m,
       aes(x = variable, y = value, fill = variable)) +
  geom_bar(stat="identity", color = "black", alpha = 0.6) + 
  theme_bw(base_size = gg.base_size) + 
  labs(title = "Barplot of packages percentage with\nparticular dir folders present",
       x = "",
       y = "packages percentage") + 
  theme(legend.position = "none")  + 
  scale_y_continuous(labels = scales::percent)

```


```{r EDA_dirs_vs_downloads, fig.width=4.9, fig.height=4.5}

data_df$vars <- factor(as.character(data_df$demo_dir_present), 
                      levels = c(1,0),
                      labels = c("Yes", "No"))

ggplot(data_df,
       aes(x = vars, 
           y = download_cnt_365d_LOG,
           group = vars,
           fill = vars)) +
  scale_fill_manual(values = c("green", "grey")) + 
  geom_boxplot(color = "black", alpha = 0.6) + 
  theme_bw(base_size = gg.base_size) + 
  labs(title = "Boxplot of log(# of downloads over 1y)",
       x = "Has demo directory?",
       y = "log(# of downloads over 1y)") + 
  theme(legend.position = "none") + 
    coord_cartesian(ylim = c(6.2, 14))


data_df$vars <- factor(as.character(data_df$src_dir_present), 
                      levels = c(1,0),
                      labels = c("Yes", "No"))

ggplot(data_df,
       aes(x = vars, 
           y = download_cnt_365d_LOG,
           group = vars,
           fill = vars)) +
  scale_fill_manual(values = c("green", "grey")) + 
  geom_boxplot(color = "black", alpha = 0.6) + 
  theme_bw(base_size = gg.base_size) + 
  labs(title = "Boxplot of log(# of downloads over 1y)",
       x = "Has src directory?",
       y = "log(# of downloads over 1y)") + 
  theme(legend.position = "none") + 
    coord_cartesian(ylim = c(6.2, 14))


data_df$vars <- factor(as.character(data_df$testthat_dir_present), 
                      levels = c(1,0),
                      labels = c("Yes", "No"))

ggplot(data_df,
       aes(x = vars, 
           y = download_cnt_365d_LOG,
           group = vars,
           fill = vars)) +
  scale_fill_manual(values = c("green", "grey")) + 
  geom_boxplot(color = "black", alpha = 0.6) + 
  theme_bw(base_size = gg.base_size) + 
  labs(title = "Boxplot of log(# of downloads over 1y)",
       x = "Has testthat directory?",
       y = "log(# of downloads over 1y)") + 
  theme(legend.position = "none") + 
    coord_cartesian(ylim = c(6.2, 14))
  

```







