---
title: 'Modeling: random forest'
author: 
- "Daniel Antiporta"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---


```{r, include = FALSE}
#rm(list = ls())
knitr::opts_chunk$set(include = TRUE, comment = NA, cache = TRUE, 
                      message = FALSE, warning = FALSE)

```

* Define project folder `712-final_project` path. That is, modify `project.dir` string below; once it points to your `712-final_project` folder location, all other stuff below would work. 

```{r, messsage= FALSE, warning=FALSE}
user.name <- Sys.info()[7]
if(user.name=="antiporta") project.dir <- "/Users/antiporta/Dropbox/712-final_project/"
if(user.name=="dantipor") project.dir <- "C://Users//dantipor//Dropbox//712-final_project/"

library(caret)
library(dplyr)
library(reshape2)
library(ggplot2)
library(fastDummies)
library(janitor)
library(tidyverse)
```


# Read data 

```{r}

out.path <- file.path(project.dir, "data/final_dfs/data_x.csv")
x_df0 <- read.csv(out.path, stringsAsFactors = FALSE)
#head(x_df0)

out.path <- file.path(project.dir, "data/final_dfs/data_y.csv")
y_df0 <- read.csv(out.path, stringsAsFactors = FALSE)
#head(y_df0)

```

# Mutate data 

### Create subset of columns of `x` data which will be used in modelling

```{r}
x_df0 <- 
  x_df0 %>% 
  select(-pkg_name,
         -rversion_min)

names(x_df0)[apply(x_df0, 2, function(col) any(is.na(col)))]
x_df0[is.na(x_df0)] <- 0
names(x_df0)[apply(x_df0, 2, function(col) any(is.na(col)))]
x_df <- x_df0
```


### Create dummy variables for subset of columns of `x`

```{r}
## x_df_license_group
x_df_license_group <- x_df %>% select(license_group)
x_df_license_group_DUMMY <- 
  dummy_cols(x_df_license_group,
             remove_most_frequent_dummy = TRUE) %>%
  select(-license_group)
x_df_license_group_DUMMY <- as.data.frame(clean_names(x_df_license_group_DUMMY))
x_df <- cbind(x_df %>% select(-license_group),
              x_df_license_group_DUMMY)

x_df <- scale(x_df, center = TRUE, scale = TRUE)
x_df <- as.data.frame(x_df)

## Sanity check
table(sapply(x_df, class))

```

### Mutate columns of `y` 

```{r}
y_df <- 
  y_df0 %>%
  select(-pkg_name) %>%
  mutate(download_cnt_90d_LOG = log(download_cnt_90d),
         download_cnt_365d_LOG = log(download_cnt_365d))
# y_df <- scale(y_df, center = TRUE, scale = TRUE)
y_df <- as.data.frame(y_df)

```


### Create data split 

```{r}
set.seed(56299)
trainIndex <- createDataPartition(y_df$download_cnt_90d, 
                                  p = 0.7, 
                                  list = FALSE, 
                                  times = 1)
#head(trainIndex[, 1], 100)
mean(head(trainIndex[, 1], 100))

## Define the train and test set                                  
x_df_TRAIN <- x_df[trainIndex, ]
x_df_TEST  <- x_df[-trainIndex, ]
y_df_TRAIN <- y_df[trainIndex, ]
y_df_TEST  <- y_df[-trainIndex, ]

dim(x_df_TRAIN); dim(x_df_TEST)
dim(y_df_TRAIN); dim(y_df_TEST)

```

# Quickly explore the data 

```{r}
#Scale and Centered X Data
x_df.cor <- as.data.frame(cor(x_df))
x_df.cor$var1 <- rownames(x_df.cor)
x_df.cor <- x_df.cor %>% melt(id.vars = "var1")
## Create label 
x_df.cor_names_sorted <- as.data.frame(t(apply(x_df.cor[, 1:2], 1, sort))) 
x_df.cor_label <- paste0(x_df.cor_names_sorted[, 1], "_", x_df.cor_names_sorted[, 2])
x_df.cor$label <- x_df.cor_label
## Discard duplicates
x_df.cor.FINAL <- 
  x_df.cor %>%
  filter(var1 != variable) %>%
  select(label, value) %>%
  distinct() %>%
  arrange(desc(abs(value)))

boxplot(x_df.cor.FINAL$value, main = "Boxplot of correlation values")

```


# Model outcome: `download_cnt_90d_LOG`

- Model-specific objects

```{r fit_rf_model_90}

## Data 
train_set_1 <- cbind(y_df_TRAIN %>% select(y = download_cnt_90d_LOG),
                     x_df_TRAIN)
test_set_1 <- cbind(y_df_TEST %>% select(y = download_cnt_90d_LOG),
                    x_df_TEST)

## Control object
set.seed(123)
train_control <- trainControl(method = "cv", 
                              number = 10)
metric <- "RMSE"

#DEFAULT
mtry <- floor(sqrt(ncol(train_set_1[-1])*0.7))
tunegrid <- expand.grid(.mtry=mtry)

set.seed(123)
start <- proc.time()[3]
rf_default <-train(y~., data=train_set_1, method="rf",
                   tuneGrid= tunegrid, trControl=train_control,
                   importance=TRUE)
end <- proc.time()[3]
print(paste("This took ", round(end-start,digits = 1), " seconds", sep = ""))
print(rf_default)

#Automatic TUNING
start <- proc.time()[3]
rf_standard <-train(y~., data=train_set_1, method="rf", 
                   trControl=train_control,
                   importance=TRUE)
end <- proc.time()[3]
print(paste("This took ", round(end-start,digits = 1), " seconds", sep = ""))
print(rf_standard)

#Number of trees TUNING
set.seed(123)
train_control <- trainControl(method="cv", 
  number=10, 
  search="grid")
tunegrid <- expand.grid(.mtry=mtry)
modellist <- list()
for (ntree in c(50, 100, 500, 1000, 1500)) {
  set.seed(123)
  fit <- train(y~., data=train_set_1, 
    method="rf", metric=metric, 
    tuneGrid=tunegrid, trControl=train_control, 
    ntree=ntree,importance=TRUE)
  key <- toString(ntree)
  modellist[[key]] <- fit
}
```

###Get Models for 90 days download

```{r save_rf_model_90}
model90_default<-rf_default
model90_auto<-rf_standard
model90_tree50<-modellist[1]$`50`
model90_tree100<-modellist[2]$`100`
model90_tree500<-modellist[3]$`500`
model90_tree1000<-modellist[4]$`1000`
model90_tree2000<-modellist[5]$`1500`
files90<-c("model90_default",
            "model90_auto",
            "model90_tree50",
            "model90_tree100",
            "model90_tree500",
            "model90_tree1000",
            "model90_tree2000")
for (i in files90){
  saveRDS(i, 
    file = paste0(project.dir, 
                "Rmd_files/2018-12-09-modeling_random_forest/",
                i))
}

#Plot tuning parameters for AUTO model
plot(model90_auto)

#Get Perfomance df
list90<-lapply(1:length(files90), function(i){
  results_i<-get(unique(files90[i])[1])$results
  results_i<-results_i %>% as.data.frame() %>%
    mutate(type=files90[i])
})
results.list90 <- do.call(rbind.data.frame, list90 )
results.list90 <- results.list90 %>% separate(type, c("model", "type"), "_")
results.list90
saveRDS(results.list90, 
    file = paste0(project.dir, 
                "Rmd_files/2018-12-09-modeling_random_forest/results_list90"))
```

### Investigate variable importance

```{r model_rf_model_90_var_importance, fig.width=8, fig.height=10}

rank_max <- 14
importance90_list<-lapply(1:length(files90), function(i){
  importance_df_i <- varImp(get(files90[i]))
  importance_df_i <- importance_df_i["importance"] %>% as.data.frame() %>%
    rownames_to_column(var = "var") %>% arrange(desc(Overall)) %>%
     filter(row_number() <= rank_max) %>% as.data.frame() %>%
    mutate(var=factor(as.character(var),
                              levels = rev(var)))
})
names(importance90_list)<-gsub("model90_", "", unique(files90))
saveRDS(importance90_list, 
    file = paste0(project.dir, 
                "Rmd_files/2018-12-09-modeling_random_forest/importance90_list"))

##Plot
for (i in 1:7){
 p_i<-ggplot(importance90_list[[i]], aes(x = var, y = Overall)) + 
    geom_bar(stat = "identity") + 
    coord_flip() + 
    theme_gray(base_size = 16) + 
    labs(title = "Variable importance from random forest for y = log(# of downloads in 90 days)\nfor top 14 important variables",
         subtitle = paste0("Model: ", names(importance90_list[i])),
         x = "Variable name",
         y = "Variable importance from random forest") + 
    theme(legend.position = "none") 
 print(p_i)
}
```

### Predictions: Fit to the test data 

```{r prediction_rf_model_90}
#Prediction Results
plt.df.90<-vector(length=length(files90), mode = "list")
names(plt.df.90)<-unique(files90)
RMSE.list90<-vector(length=length(files90))
r2.tmp.list90<-vector(length=length(files90))
MSE.tmp.list90<-vector(length=length(files90))
res.tmp.list90<-vector(length=length(files90))
for (i in 1:length(files90)){
  predictions_i <- predict(get(files90[i]), test_set_1[-1])
  plt.df_i <- data.frame(pred = predictions_i, obs = test_set_1[, 1])
  plt.df.90[[i]] <-as.tibble(plt.df_i)
  RMSE.list90[i] <- 
    sqrt(sum((predictions_i - test_set_1$y)^2)/length(predictions_i))
  resid.tmp.list90_i <- plt.df_i$obs - plt.df_i$pred
  res.tmp.list90[i] <-as.tibble(resid.tmp.list90_i)
  SS.total.list90 <- sum((plt.df_i$obs - mean(plt.df_i$obs))^2)
  SS.regression.list90 <- sum((plt.df_i$pred-mean(plt.df_i$obs))^2)
  SS.residual.list90   <- sum(resid.tmp.list90_i^2)
  r2.tmp.list90[i] <- SS.regression.list90/SS.total.list90
  MSE.tmp.list90[i] <- mean((resid.tmp.list90_i)^2)
}
prediction.list90<-cbind.data.frame(files90, 
                                    RMSE.list90,
                                    r2.tmp.list90,
                                    MSE.tmp.list90)
prediction.list90<-prediction.list90 %>%
  separate(files90, c("model", "type"), "_")
prediction.list90
saveRDS(prediction.list90, 
    file = paste0(project.dir, 
                "Rmd_files/2018-12-09-modeling_random_forest/prediction_list90"))
```

```{r model_rf_model_1_pred, fig.width= 6, fig.height=5}
## plot 1 
for (i in 1:7){
p<-ggplot(plt.df.90[[i]], aes(x = obs, y = pred)) + 
  geom_point(alpha = 0.7) + 
  labs(title = paste0("Model predictions for y = log(# of downloads in 90 days)"),
  	   subtitle= bquote("MSE: "~ .(round(MSE.tmp.list90[[i]], 3))~
  	                      ","~r^{2}~": "~ .(round(r2.tmp.list90[[i]], 3))),
       caption = paste0("Model: ", (gsub("model90_", "", names(plt.df.90[i])))),
       x = "observed",
       y = "predicted") + 
  geom_abline(intercept = 0, slope = 1, color="red", 
              linetype="dashed", size=1.5) + 
  theme_gray(base_size = 12)
print(p)
}
for (i in 1:7){
## plot 2
data_plot<-cbind(plt.df.90[[i]], res.tmp.list90[[i]])
names(data_plot)<-c("pred", "obs", "resid.tmp")
q<-ggplot(data_plot, aes(x = obs, y = resid.tmp)) + 
  geom_point(alpha= 0.7) + 
  labs(title = paste0("Model residuals for y = log(# of downloads in 90 days)"),
  	   subtitle= bquote("MSE: "~ .(round(MSE.tmp.list90[[i]], 3))~
  	                      ","~r^{2}~": "~ .(round(r2.tmp.list90[[i]], 3))),
       caption = paste0("Model: ", (gsub("model90_", "", names(plt.df.90[i])))),
       x = "observed",
       y = "residual (y - hat{y})") + 
  geom_abline(intercept = 0, slope = 0, color="red", 
              linetype="dashed", size=1.5)+ 
  theme_gray(base_size = 12) 
print(q)
}
```

# Model outcome: `download_cnt_365d_LOG`

- Model-specific objects

```{r fit_rf_model_360}
## Data 
train_set_2 <- cbind(y_df_TRAIN %>% select(y = download_cnt_365d_LOG),
                     x_df_TRAIN)
test_set_2 <- cbind(y_df_TEST %>% select(y = download_cnt_365d_LOG),
                    x_df_TEST)

## Control object
set.seed(123)
train_control_2 <- trainControl(method = "cv", 
                              number = 10)
metric <- "RMSE"

#DEFAULT
mtry <- floor(sqrt(ncol(train_set_2[-1])*0.7))
tunegrid <- expand.grid(.mtry=mtry)

set.seed(123)
start <- proc.time()[3]
rf_default_2 <-train(y~., data=train_set_2, method="rf", 
  metric=metric, tuneGrid= tunegrid, trControl=train_control_2,
                   importance=TRUE)
end <- proc.time()[3]
print(paste("This took ", round(end-start,digits = 1), " seconds", sep = ""))
print(rf_default_2)
#plot(rf_default_2)

predictions.default_2 <- predict(rf_default_2, test_set_2[-1])
RMSE.default_2 <- sqrt(sum((predictions.default_2 - test_set_2$y)^2)/length(predictions.default_2))
print(RMSE.default_2)
#plot(RMSE.default_2$finalModel)

#Automatic TUNING
start <- proc.time()[3]
rf_standard_2 <-train(y~., data=train_set_2, method="rf", 
 trControl=train_control_2,
                   importance=TRUE)
end <- proc.time()[3]
print(paste("This took ", round(end-start,digits = 1), " seconds", sep = ""))
print(rf_standard_2)
#plot(rf_standard_2)

predictions.standard_2 <- predict(rf_standard_2, test_set_2[-1])
RMSE.standard_2 <- sqrt(sum((predictions.standard_2 - test_set_2$y)^2)/length(predictions.standard_2))
print(RMSE.standard_2)
#plot(RMSE.standard_2$finalModel)

#Number of trees TUNING
set.seed(123)
train_control_2 <- trainControl(method="cv", 
  number=10, 
  search="grid")
tunegrid <- expand.grid(.mtry=mtry)
modellist_2 <- list()
for (ntree in c(50, 100, 500, 1000, 1500, 2000, 2500)) {
  set.seed(123)
  fit <- train(y~., data=train_set_2, 
    method="rf", metric=metric, 
    tuneGrid=tunegrid, trControl=train_control_2, 
    ntree=ntree,importance=TRUE)
  key <- toString(ntree)
  modellist_2[[key]] <- fit
}
```

###Get Models for 360 days download

```{r save_rf_model_360}
model360_default<-rf_default_2
model360_auto<-rf_standard_2
model360_tree50<-modellist_2[1]$`50`
model360_tree100<-modellist_2[2]$`100`
model360_tree500<-modellist_2[3]$`500`
model360_tree1000<-modellist_2[4]$`1000`
model360_tree2000<-modellist_2[5]$`1500`
files360<-c("model360_default",
            "model360_auto",
            "model360_tree50",
            "model360_tree100",
            "model360_tree500",
            "model360_tree1000",
            "model360_tree2000")
for (i in files360){
  saveRDS(i, 
    file = paste0(project.dir, 
                "Rmd_files/2018-12-09-modeling_random_forest/",
                i))
}

#Plot tuning parameters for AUTO model
plot(model360_auto)

#Get Perfomance df
list360<-lapply(1:length(files360), function(i){
  results_i<-get(unique(files360[i])[1])$results
  results_i<-results_i %>% as.data.frame() %>%
    mutate(type=files360[i])
})
results.list360 <- do.call(rbind.data.frame, list360)
results.list360 <- results.list360 %>% separate(type, c("model", "type"), "_")
results.list360
saveRDS(results.list360, 
    file = paste0(project.dir, 
                "Rmd_files/2018-12-09-modeling_random_forest/results_list360"))

```

### Investigate variable importance

```{r model_rf_model_360_var_importnace, fig.width=8, fig.height=10}
rank_max <- 14
importance360_list<-lapply(1:length(files360), function(i){
  importance_df_i <- varImp(get(files360[i]))
  importance_df_i <- importance_df_i["importance"] %>% as.data.frame() %>%
    rownames_to_column(var = "var") %>% arrange(desc(Overall)) %>%
     filter(row_number() <= rank_max) %>% as.data.frame() %>%
    mutate(var=factor(as.character(var),
                              levels = rev(var)))
})
names(importance360_list)<-gsub("model360_", "", unique(files360))
saveRDS(importance360_list, 
    file = paste0(project.dir, 
                "Rmd_files/2018-12-09-modeling_random_forest/importance360_list"))

##Plot
for (i in 1:7){
 p_i<-ggplot(importance360_list[[i]], aes(x = var, y = Overall)) + 
    geom_bar(stat = "identity") + 
    coord_flip() + 
    theme_gray(base_size = 16) + 
    labs(title = "Variable importance from random forest for y = log(# of downloads in 360 days)\nfor top 14 important variables",
         subtitle = paste0("Model: ", names(importance360_list[i])),
         x = "Variable name",
         y = "Variable importance from random forest") + 
    theme(legend.position = "none") 
 print(p_i)
}
```

### Predictions: Fit to the test data 

```{r prediction_rf_model_360}
#Prediction Results
plt.df.360<-vector(length=length(files360), mode = "list")
names(plt.df.360)<-unique(files360)
RMSE.list360<-vector(length=length(files360))
r2.tmp.list360<-vector(length=length(files360))
MSE.tmp.list360<-vector(length=length(files360))
res.tmp.list360<-vector(length=length(files360))

for (i in 1:length(files360)){
  predictions_i <- predict(get(files360[i]), test_set_2[-1])
  plt.df_i <- data.frame(pred = predictions_i, obs = test_set_2[, 1])
  plt.df.360[[i]] <-as.tibble(plt.df_i)
  RMSE.list360[i] <- 
    sqrt(sum((predictions_i - test_set_2$y)^2)/length(predictions_i))
  resid.tmp.list360 <- plt.df_i$obs - plt.df_i$pred
  res.tmp.list360[i] <-as.tibble(resid.tmp.list360)
  SS.total.list360 <- sum((plt.df_i$obs - mean(plt.df_i$obs))^2)
  SS.regression.list360 <- sum((plt.df_i$pred-mean(plt.df_i$obs))^2)
  SS.residual.list360   <- sum(resid.tmp.list360^2)
  r2.tmp.list360[i] <- SS.regression.list360/SS.total.list360
  MSE.tmp.list360[i] <- mean((resid.tmp.list360)^2)
}
prediction.list360<-cbind.data.frame(files360, 
                                    RMSE.list360,
                                    r2.tmp.list360,
                                    MSE.tmp.list360)
prediction.list360<-prediction.list360 %>%
  separate(files360, c("model", "type"), "_")
prediction.list360
saveRDS(prediction.list360, 
    file = paste0(project.dir, 
                "Rmd_files/2018-12-09-modeling_random_forest/prediction_list360"))

```

```{r model_rf_model_2_pred, fig.width= 6, fig.height=5}
## plot 1 
for (i in 1:7){
p<-ggplot(plt.df.360[[i]], aes(x = obs, y = pred)) + 
  geom_point(alpha = 0.7) + 
  labs(title = paste0("Model predictions for y = log(# of downloads in 1 year)"),
  	   subtitle= bquote("MSE: "~ .(round(MSE.tmp.list360[[i]], 3))~
  	                      ","~r^{2}~": "~ .(round(r2.tmp.list360[[i]], 3))),
       caption = paste0("Model: ", (gsub("model360_", "", names(plt.df.360[i])))),
       x = "observed",
       y = "predicted") + 
  geom_abline(intercept = 0, slope = 1, color="red", 
              linetype="dashed", size=1.5) +
    theme_gray(base_size = 12)
print(p)
}
for (i in 1:7){
## plot 2
data_plot<-cbind(plt.df.360[[i]], res.tmp.list360[[i]])
names(data_plot)<-c("pred", "obs", "resid.tmp")
q<-ggplot(data_plot, aes(x = obs, y = resid.tmp)) + 
  geom_point(alpha = 0.7) + 
  labs(title = paste0("Model residuals for y = log(# of downloads in 360 days)"),
  	   subtitle= bquote("MSE: "~ .(round(MSE.tmp.list360[[i]], 3))~
  	                      ","~r^{2}~": "~ .(round(r2.tmp.list360[[i]], 3))),
       caption = paste0("Model: ", (gsub("model360_", "", names(plt.df.360[i])))),
       x = "observed",
       y = "residual (y - hat{y})") + 
  geom_abline(intercept = 0, slope = 0, color="red", 
              linetype="dashed", size=1.5) + 
  theme_gray(base_size = 12)
print(q)
}
```

### Best Model for 360d downloads-PLOTS

-Ranfom Forest with `mtry`=101 and `ntree`=1000

```{r model_rf_model_2_pred_hmw, fig.width= 5, fig.height=5, echo=FALSE}
model_360_pred_final <- predict(model360_auto,
                        newdata = test_set_2[, -1])

plt.df_360_final <- data.frame(pred = model_360_pred_final, obs = test_set_2[, 1])

## plot 1 
resid.tmp <- plt.df_360_final$obs - plt.df_360_final$pred
SS.total      <- sum((plt.df_360_final$obs - mean(plt.df_360_final$obs))^2)
SS.regression <- sum((plt.df_360_final$pred-mean(plt.df_360_final$obs))^2)
SS.residual   <- sum(resid.tmp^2)
r2.tmp <- SS.regression/SS.total
MSE.tmp <- mean((resid.tmp)^2)

ggplot(plt.df_360_final, aes(x = obs, y = pred)) + 
  geom_point(alpha = 0.7) + 
  labs(title = paste0("Predictions of log(# of downloads in 1y)"),
  	   subtitle= bquote("MSE: "~ .(round(MSE.tmp, 3))~
  	                      ","~r^{2}~": "~ .(round(r2.tmp, 3))),
       caption = paste0("Model: Tree 1000"),
       x = "observed",
       y = "predicted") + 
  theme(title =element_text(size=16)) +
  geom_abline(intercept = 0, slope = 1, color="red", 
              linetype="dashed", size=1.5)  + 
  theme_gray(base_size = 12)


## plot 2
plt.df_360_final$resid <- resid.tmp
ggplot(plt.df_360_final, aes(x = obs, y = resid.tmp)) + 
  geom_point() + 
  labs(title = paste0("Model residuals for y = log(# of downloads in 1y) \n(red line: y = 0)"),
  	   subtitle= bquote("MSE: "~ .(round(MSE.tmp, 3))~
  	                      ","~r^{2}~": "~ .(round(r2.tmp, 3))),
       caption = paste0("Model: Tree 1000"),
       x = "observed",
       y = "residual (y - hat{y})") +
  theme(title =element_text(size=12, face='bold')) +
  theme(title =element_text(size=16)) +
  geom_abline(intercept = 0, slope = 0, color="red", 
              linetype="dashed", size=1.5)  + 
  theme_gray(base_size = 12)
```

```{r model_rf_model_2_var_importance, fig.width=10, fig.height=10, echo=FALSE}
#Var Importance
rank_max <- 14
importance_df_360 <- varImp(model360_auto)$importance
importance_df_360$var <- rownames(importance_df_360)
rownames(importance_df_360) <- NULL
importance_df_360 <- 
  importance_df_360 %>%
  arrange(desc(Overall)) %>%
  filter(row_number() <= rank_max) %>%
  as.data.frame()
importance_df_360$var <- factor(as.character(importance_df_360$var),
                            levels = rev(importance_df_360$var))

##plot
ggplot(importance_df_360, aes(x = var, y = Overall)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  theme_gray(base_size = 16) + 
  labs(title = "Top Variable importance",
       x = "Variable name",
       y = "Variable importance") + 
  theme(legend.position = "none",
        axis.text = element_text(size=22), 
        title = element_text(size=26),
        axis.title = element_text(size=24))
```

```{r top_variables_for_models, fig.width=10, fig.height=10, echo=FALSE}
##plot
rank.max <- 10
model_1_var.df.SUB <- 
  importance90_list$tree1000 %>%
  mutate(outcome = "log(# of downloads in 90 days)",
         var_rank = rank(desc(abs(Overall)))) %>%
  arrange(var_rank) 

model_2_var.df.SUB <- 
  importance_df_360 %>%
  mutate(outcome = "log(# of downloads in 360 days)",
         var_rank = rank(desc(abs(Overall)))) %>%
  arrange(var_rank) 

keep.vars <- union(model_1_var.df.SUB$var[1:rank.max], 
                   model_2_var.df.SUB$var[1:rank.max])
model_var.final <- 
  rbind(model_1_var.df.SUB,
        model_2_var.df.SUB) %>%
  filter(var %in% keep.vars)

model_var.final.agg <- 
  model_var.final %>%
  group_by(var) %>%
  summarise(val_abs_max = max(abs(Overall))) %>%
  arrange(val_abs_max) %>%
  as.data.frame()
model_var.final$var <- factor(as.character(model_var.final$var),
                               levels = model_var.final.agg$var)
model_var.final$group = sign(model_var.final$Overall )

outcome.unique <- sort(unique(as.character(model_var.final$outcome)))
model_var.final$outcome <- factor(as.character(model_var.final$outcome),
                               levels = c(outcome.unique[1], outcome.unique[2]))

ggplot(model_var.final, 
       aes(x = var, y = Overall, fill = factor(group))) + 
  geom_bar(stat = "identity") + 
  facet_grid(. ~ outcome) +
  coord_flip() + 
  theme_gray(base_size = 14) + 
  labs(title = "Top variable importance (random forest)",
       y = "Variable Importance",
       x = "Variable name") + 
  theme(legend.position = "none") 
```
