---
title: 'Features engineering: task 3'
author: "Marta Karas"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: false
    toc_depth: 3
---

- vignette: pages (min / max / mean)
- reference manual: number of functions exported
- reference manual: unique number of papers cited


```{r, include = FALSE}
rm(list = ls())
knitr::opts_chunk$set(include = TRUE, comment = NA, cache = FALSE, 
                      message = FALSE, warning = FALSE)
options(stringsAsFactors=FALSE)

```

* Define project folder `712-final_project` path. That is, modify `project.dir` string below; once it points to your `712-final_project` folder location, all other stuff below would work. 

```{r}

library(rvest)
library(ggplot2)
library(dplyr)
library(future)
library(stringi)
library(tm)
library(tools)

user.name<-Sys.info()[7]
if(user.name=="antiporta") project.dir <- "/Users/antiporta/Dropbox/712-final_project/"
if(user.name=="mkaras") project.dir <- "/Users/mkaras/Dropbox/JHU/711-ADV_DATA_SCIENCE/712-final_project"
```


# Read `data.frame` with package name, package first release 

```{r}
path.tmp <- file.path(project.dir, "data/pkg_first_release_SUBSET.csv")
pkg_first_rel <- read.csv(path.tmp, stringsAsFactors = FALSE)
pkg_first_rel$first_release <- as.Date(pkg_first_rel$first_release)

## Preview
head(pkg_first_rel)
packageNames.vec <- pkg_first_rel$pkg_name
```



# 1. Get info about vignette(s)

```{r, eval = FALSE}

pkg_install_dir <- "/Users/mkaras/Documents/JHU/712-final_project_MY_WORKSPACE/data/pkg_installation_dir/"

pkg_name.i <- packageNames.vec[i]
n <- length(packageNames.vec)

plan(sequential)
# plan(multisession, workers = parallel::detectCores() - 1)

t1 <- Sys.time()
results.f <- lapply(1:n, function(i) {
  
  future({
    
    pkg_name.i <- packageNames.vec[i]
    pkg_install_dir.i <- paste0(pkg_install_dir, pkg_name.i)
    files.i <- list.files(pkg_install_dir.i, full.names = FALSE)
    
    no.vignette <- TRUE
    list_out <- list()
    
    if ("vignettes" %in% files.i){
      vignette.dir <- paste0(pkg_install_dir.i, "/vignettes")
      vignette.url.vec <- list.files(vignette.dir, full.names = TRUE)
      vignette.url.vec <- vignette.url.vec[file_ext(vignette.url.vec) %in% 
                                             c("Rnw", "Rmd", "md")]
      if (length(vignette.url.vec) > 0){
        no.vignette <- FALSE
        ## Iterate over list of vignette files
        for (j in 1:length(vignette.url.vec)){
          url   <- vignette.url.vec[j]
          text <- paste0(readLines(url), collapse = " ") 
          text <- removeNumbers(text)
          text <- removePunctuation(text)
          text <- stripWhitespace(text)
          words <- unlist(stri_extract_all_words(text))
          words <- words[nchar(words) >= 3]
          words.cnt <- length(words)
          list_out.vec <- c(pkg_name.i, 1, basename(url), words.cnt)
          list_out[[length(list_out) + 1]] <- list_out.vec
        }
      } 
    }
    
    if (no.vignette){
      list_out[[length(list_out) + 1]] <- c(pkg_name.i, 0, NA, NA)
    }
    return(list_out)
    
  }) 
}) 

results <- lapply(results.f, value)
t2 <- Sys.time()
t2 - t1

## Convert results list to a data frame 
results.df0 <- lapply(results, function(ll){
  ll <- do.call(rbind.data.frame, ll)
  names(ll) <- c("pkg_name", "pkg_vig_any", "pkg_vig_name", "words_cnt")
  ll
})
results.df <- do.call(rbind.data.frame, results.df0)
results.df$pkg_vig_any <- as.numeric(as.character(results.df$pkg_vig_any))
results.df$words_cnt <- as.numeric(as.character(results.df$words_cnt))

##  ----------------------------------------------------------------------------
## Save to file

# out.path <- file.path(project.dir, "data/pkg_vignette_info_REDO.csv")
# write.csv(results.df, out.path, row.names = FALSE, quote = FALSE)

```


# 2. Get info about exported functions number

```{r, eval = FALSE}

pkg_install_dir <- "/Users/mkaras/Documents/JHU/712-final_project_MY_WORKSPACE/data/pkg_installation_dir/"

exported_func_cnt.vec <- numeric()

n <- length(packageNames.vec)
# n <- 10
for (i in 1:n){
  pkg_name.i <- packageNames.vec[i]
  pkg_man_dir.i <- paste0(pkg_install_dir, pkg_name.i, "/man")
  pkg_man_files.i <- list.files(pkg_man_dir.i, full.names = FALSE)
  exported_func_cnt.vec[i] <- length(pkg_man_files.i)
}

exported_func_cnt.df <- 
  data.frame(pkg_name = packageNames.vec,
             exported_func_cnt = exported_func_cnt.vec,
             stringsAsFactors = FALSE)

exported_func_cnt.df %>% arrange(exported_func_cnt)

# out.path <- file.path(project.dir, "data/exported_func_cnt.csv")
# write.csv(exported_func_cnt.df, out.path, row.names = FALSE, quote = FALSE)
```




# Produce final data frame 

### 1. Vignette info

```{r}

path.tmp <- file.path(project.dir, "data/pkg_vignette_info_REDO.csv")
pkg_vignette_info <- read.csv(path.tmp, stringsAsFactors = FALSE)
## Sanity checking
any(is.na(pkg_vignette_info$pkg_vig_any))
pkg_vignette_info %>% filter(pkg_vig_any == 1, is.na(words_cnt))

df1 <- 
  pkg_vignette_info %>%
  group_by(pkg_name) %>%
  summarize(vignette_any = max(pkg_vig_any),
            vignette_cnt = sum(pkg_vig_any),
            vignette_words_cnt_min = min(words_cnt),
            vignette_words_cnt_max = max(words_cnt),
            vignette_words_cnt_mean = mean(words_cnt),
            vignette_words_cnt_median = median(words_cnt)) %>%
  as.data.frame()


```

### 2. Info about exported functions number

```{r}

path.tmp <- file.path(project.dir, "data/exported_func_cnt.csv")
exported_func_cnt <- read.csv(path.tmp, stringsAsFactors = FALSE)

## Sanity checking
dim(exported_func_cnt)
head(exported_func_cnt)
any(is.na(exported_func_cnt$exported_func_cnt))

df2 <- exported_func_cnt

```


### Merge them all together

```{r, eval = FALSE}

dim(pkg_first_rel)

df.out <- 
  pkg_first_rel %>%
  select(-first_release) %>%
  left_join(df1, by = "pkg_name") %>%
  left_join(df2, by = "pkg_name")

dim(df.out)
head(df.out)
str(df.out)

out.path <- file.path(project.dir, "data/feature_task/features_extracted_part3.csv")
write.csv(df.out, out.path, row.names = FALSE, quote = FALSE)

```











