---
title: 'Modeling: linear regression'
author: 
- "Marta Karas, Perry Kuo"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: false
    toc_depth: 3
---


```{r, include = FALSE}
rm(list = ls())
knitr::opts_chunk$set(include = TRUE, comment = NA, cache = TRUE, 
                      message = FALSE, warning = FALSE)

```

* Define project folder `712-final_project` path. That is, modify `project.dir` string below; once it points to your `712-final_project` folder location, all other stuff below would work. 

```{r}
user.name <- Sys.info()[7]
if(user.name=="antiporta") project.dir <- "/Users/antiporta/Dropbox/712-final_project/"
if(user.name=="mkaras") project.dir <- "/Users/mkaras/Dropbox/JHU/711-ADV_DATA_SCIENCE/712-final_project/"
if(user.name=="kuop2") project.dir <- "C:/Users/kuop2/Desktop/712-final_project"
if(user.name=="pkuo6") project.dir <- "C:/Users/pkuo6/Desktop/712-final_project"

library(caret)
library(dplyr)
library(reshape2)
library(ggplot2)
library(fastDummies)
library(janitor)
library(e1071)
library(kableExtra)
```


# Read data 

```{r}

out.path <- file.path(project.dir, "data/final_dfs/data_x.csv")
x_df0 <- read.csv(out.path, stringsAsFactors = FALSE)
# head(x_df0)

out.path <- file.path(project.dir, "data/final_dfs/data_y.csv")
y_df0 <- read.csv(out.path, stringsAsFactors = FALSE)
# head(y_df0)

```

# Mutate data 

### Create subset of columns of `x` data which will be used in modelling

```{r}
# apply(x_df0, 2, function(col) any(is.na(col)))
x_df0 <- 
  x_df0 %>% 
  select(-pkg_name,
         -rversion_min)

names(x_df0)[apply(x_df0, 2, function(col) any(is.na(col)))]
x_df0[is.na(x_df0)] <- 0
names(x_df0)[apply(x_df0, 2, function(col) any(is.na(col)))]
x_df <- x_df0
```


### Create dummy variables for subset of columns of `x`

```{r}
## x_df_license_group
x_df_license_group <- x_df %>% select(license_group)
x_df_license_group_DUMMY <- 
  dummy_cols(x_df_license_group,
             remove_most_frequent_dummy = TRUE) %>%
  select(-license_group)
x_df_license_group_DUMMY <- as.data.frame(clean_names(x_df_license_group_DUMMY))
x_df <- cbind(x_df %>% select(-license_group),
              x_df_license_group_DUMMY)

x_df <- scale(x_df, center = TRUE, scale = TRUE)
x_df <- as.data.frame(x_df)

## Sanity check
table(sapply(x_df, class))

```

### Mutate columns of `y` 

```{r}
y_df <- 
  y_df0 %>%
  select(-pkg_name) %>%
  mutate(download_cnt_90d_LOG = log(download_cnt_90d),
         download_cnt_365d_LOG = log(download_cnt_365d))
# y_df <- scale(y_df, center = TRUE, scale = TRUE)
y_df <- as.data.frame(y_df)

```


### Create data split 

```{r}
set.seed(56299)
trainIndex <- createDataPartition(y_df$download_cnt_90d, 
                                  p = 0.7, 
                                  list = FALSE, 
                                  times = 1)
head(trainIndex[, 1], 100)
mean(head(trainIndex[, 1], 100))

## Define the train and test set                                  
x_df_TRAIN <- x_df[trainIndex, ]
x_df_TEST  <- x_df[-trainIndex, ]
y_df_TRAIN <- y_df[trainIndex, ]
y_df_TEST  <- y_df[-trainIndex, ]

dim(x_df_TRAIN); dim(x_df_TEST)
dim(y_df_TRAIN); dim(y_df_TEST)

```



# Model outcome: `download_cnt_90d_LOG`

- Model-specific objects

```{r}

## Data 
train_set_1 <- cbind(y_df_TRAIN %>% select(y = download_cnt_90d_LOG),
                     x_df_TRAIN) 
train_set_1 <- 
  train_set_1 %>%
  select(-starts_with("license_"))

test_set_1 <- cbind(y_df_TEST %>% select(y = download_cnt_90d_LOG),
                    x_df_TEST)
test_set_1 <- 
  test_set_1 %>%
  select(-starts_with("license_"))

## Model
model_1 <- lm(data = train_set_1, formula = y ~ .)

```


### SVM fit: `svmLinear`

* Continue with cv only, but use some wider grid of params.

* We start with using a random parameter. Here, we use tuneLength = 10 random values.

```{r model_1a, eval = FALSE}

set.seed(56299)

train_control <- trainControl(method = "cv", 
                              number = 10)
t1 <- Sys.time()
model_1_svmLinear <- train(formula(model_1), 
                       data = train_set_1, 
                       method = "svmLinear",
                       trControl = train_control,
                       preProcess = c("center", "scale"),
                       tuneLength = 100)
t2 <- Sys.time()
t2 - t1

res.df <- model_1_svmLinear$results
# head(res.df %>% arrange(RMSE))

model_1_svmLinear$results %>% 
  arrange(desc(-RMSE)) %>%
  head(.,10) %>%
  kable() %>%
  kable_styling()

#   C     RMSE   Rsquared       MAE    RMSESD RsquaredSD      MAESD
# 1 1 0.722706 0.04022233 0.4900344 0.1022609 0.03113255 0.03538215


```

- Ok, so for linear SVM there is no more than one parameter, really :D

* Tune the parameter.

```{r model_svm_linear_grid, eval = FALSE}

set.seed(56299)


train_control <- trainControl(method = "cv", 
                              number = 10)

# grid <- expand.grid(C = c(1:101,by = 10) ) # more than 2 hours!!!

grid <- expand.grid(C = c(1:10)) 

t3 <- Sys.time()
model_1_svmLinear_grid <- train(formula(model_1), 
                       data = train_set_1, 
                       method = "svmLinear",
                       tuneGrid = grid,
                       trControl = train_control,
                       preProcess = c("center", "scale"),
                       tuneLength = 100)
t4 <- Sys.time()
t4 - t3

res.df <- model_1_svmLinear$results
head(res.df %>% arrange(RMSE))

model_1_svmLinear_grid$results %>% 
  arrange(desc(-RMSE)) %>%
  head(.,10) %>%
  kable() %>%
  kable_styling()
```


```{r  model_svm_linear_grid_plot, eval = FALSE}
plot(model_1_svmLinear_grid)

```

### SVM fit: `svmRadial` 

```{r model_svm_radial, eval = FALSE}

set.seed(56299)

train_control <- trainControl(method = "cv", 
                              number = 10)

t1 <- Sys.time()
model_1_svmRadial <- train(formula(model_1), 
                       data = train_set_1, 
                       method = "svmRadial",
                       trControl = train_control,
                       preProcess = c("center", "scale"),
                       tuneLength = 10)
t2 <- Sys.time()
t2 - t1

res.df <- model_1_svmRadial$results
head(res.df %>% arrange(RMSE))

#         sigma    C      RMSE   Rsquared       MAE     RMSESD RsquaredSD      MAESD
# 1 0.004280896 0.50 0.6669842 0.07081315 0.4590531 0.09755935 0.04327783 0.02444249
# 2 0.004280896 1.00 0.6676132 0.06782853 0.4634098 0.09571234 0.04084600 0.02587064
# 3 0.004280896 0.25 0.6686870 0.07286581 0.4568060 0.09933987 0.04652760 0.02468617
# 4 0.004280896 2.00 0.6691872 0.06598689 0.4695027 0.09352046 0.03902073 0.02750277
# 5 0.004280896 4.00 0.6705562 0.06793364 0.4762278 0.09079571 0.03535220 0.02904918
# 6 0.004280896 8.00 0.6751716 0.07305942 0.4874912 0.08695206 0.03308952 0.02909055

```


```{r model_svm_radial_grid1, eval = FALSE}

grid01 <- expand.grid(sigma = c(1:10)/1000,
                    C = c(1:20)/10)
set.seed(56299)

train_control <- trainControl(method = "cv", 
                              number = 10)

t7 <- Sys.time()
model_1_svmRadial_grid01 <- train(formula(model_1), 
                       data = train_set_1, 
                       method = "svmRadial",
                       tuneGrid = grid01,
                       trControl = train_control,
                       preProcess = c("center", "scale"),
                       tuneLength = 100)
t8 <- Sys.time()
t8 - t7


res.df <- model_1_svmRadial_grid01$results
head(res.df %>% arrange(RMSE))

#   sigma   C      RMSE   Rsquared       MAE     RMSESD RsquaredSD      MAESD
# 1 0.003 0.5 0.6666442 0.07232319 0.4585946 0.09705640 0.04395173 0.02434944
# 2 0.003 0.6 0.6666699 0.07144018 0.4594943 0.09669255 0.04333117 0.02445332
# 3 0.003 0.4 0.6667221 0.07352120 0.4575109 0.09761158 0.04420596 0.02436945
# 4 0.004 0.5 0.6668127 0.07130159 0.4589431 0.09737622 0.04340887 0.02436964
# 5 0.004 0.4 0.6668817 0.07248381 0.4579169 0.09802014 0.04405495 0.02429607
# 6 0.007 2.0 0.6669222 0.06478342 0.4699896 0.09452205 0.03278296 0.02791414
```

```{r  model_svm_radial_grid1_plot, fig.width= 12, fig.height=8}
model_1_svmRadial_grid01$results %>% 
  arrange(desc(-RMSE)) %>%
  head(.,10) %>%
  kable() %>%
  kable_styling()

plot(model_1_svmRadial_grid01)
```
* limit grid - first one
```{r model_svm_radial_grid2, eval = FALSE, cache=TRUE}

grid01 <- expand.grid(sigma = c(30:40)/10000,
                    C = c(45:55)/100)
set.seed(56299)

train_control <- trainControl(method = "cv", 
                              number = 10)

t9 <- Sys.time()
model_1_svmRadial_grid02 <- train(formula(model_1), 
                       data = train_set_1, 
                       method = "svmRadial",
                       tuneGrid = grid01,
                       trControl = train_control,
                       preProcess = c("center", "scale"),
                       tuneLength = 100)
t10 <- Sys.time()
t10 - t9

res.df <- model_1_svmRadial_grid02$results
head(res.df %>% arrange(RMSE))

#   sigma   C      RMSE   Rsquared       MAE     RMSESD RsquaredSD      MAESD
# 1 0.0033 0.53 0.6665542 0.07206463 0.4589384 0.09702114 0.04368157 0.02436655
# 2 0.0033 0.54 0.6665568 0.07197168 0.4590096 0.09697926 0.04358042 0.02437365
# 3 0.0033 0.52 0.6665569 0.07215393 0.4588579 0.09705393 0.04373884 0.02434863
# 4 0.0034 0.51 0.6665612 0.07216867 0.4587972 0.09712722 0.04370221 0.02433999
# 5 0.0034 0.52 0.6665632 0.07206929 0.4588799 0.09708861 0.04364388 0.02435200
# 6 0.0033 0.51 0.6665640 0.07223102 0.4587794 0.09708975 0.04380084 0.02433721
```

```{r  model_svm_radial_grid2_plot, fig.width= 12, fig.height=8}
model_1_svmRadial_grid02$results %>% 
  arrange(desc(-RMSE)) %>%
  head(.,10) %>%
  kable() %>%
  kable_styling()

plot(model_1_svmRadial_grid02)
```

* limit grid - second one 
```{r model_svm_radial_grid3, eval = FALSE, cache=TRUE}

grid01 <- expand.grid(sigma = c(75:95)/10000,
                    C = c(19:59)/100)
set.seed(56299)

train_control <- trainControl(method = "cv", 
                              number = 10)

t9 <- Sys.time()
model_1_svmRadial_grid03 <- train(formula(model_1), 
                       data = train_set_1, 
                       method = "svmRadial",
                       tuneGrid = grid01,
                       trControl = train_control,
                       preProcess = c("center", "scale"),
                       tuneLength = 100)
t10 <- Sys.time()
t10 - t9

res.df <- model_1_svmRadial_grid03$results
head(res.df %>% arrange(RMSE))

#   sigma   C      RMSE   Rsquared       MAE     RMSESD RsquaredSD      MAESD

```

```{r  model_svm_radial_grid3_plot, fig.width= 12, fig.height=8}
model_1_svmRadial_grid03$results %>% 
  arrange(desc(-RMSE)) %>%
  head(.,10) %>%
  kable() %>%
  kable_styling()

plot(model_1_svmRadial_grid03)
```


* limit grid - third one 
```{r model_svm_radial_grid4, eval = FALSE, cache=TRUE}

grid01 <- expand.grid(sigma = c(75:95)/10000,
                    C = c(19:59,by = 5)/10)
set.seed(56299)

train_control <- trainControl(method = "cv", 
                              number = 10)

t9 <- Sys.time()
model_1_svmRadial_grid04 <- train(formula(model_1), 
                       data = train_set_1, 
                       method = "svmRadial",
                       tuneGrid = grid01,
                       trControl = train_control,
                       preProcess = c("center", "scale"),
                       tuneLength = 100)
t10 <- Sys.time()
t10 - t9

res.df <- model_1_svmRadial_grid04$results
head(res.df %>% arrange(RMSE))

#   sigma   C      RMSE   Rsquared       MAE     RMSESD RsquaredSD      MAESD

```


```{r  model_svm_radial_grid4_plot, fig.width= 12, fig.height=8}
model_1_svmRadial_grid04$results %>% 
  arrange(desc(-RMSE)) %>%
  head(.,10) %>%
  kable() %>%
  kable_styling()

plot(model_1_svmRadial_grid04)
```

- Refit above with selected params 

```{r model_1_svm_fit}

set.seed(56299)

train_control <- trainControl(method = "cv", 
                              number = 10)

tuneGrid <- expand.grid(.sigma = 0.0038, 
                        .C = 0.55)

t1 <- Sys.time()
model_1_svmRadial <- train(formula(model_1), 
                       data = train_set_1, 
                       method = "svmRadial",
                       trControl = train_control,
                       preProcess = c("center", "scale"),
                       tuneGrid = tuneGrid)
t2 <- Sys.time()
t2 - t1
# Time difference of 12.14971 secs

res.df <- model_1_svmRadial$results
head(res.df %>% arrange(RMSE))
#    sigma    C      RMSE   Rsquared       MAE     RMSESD RsquaredSD      MAESD
# 1 0.0033 0.53 0.6653641 0.08002368 0.4560145 0.08063083 0.03182393 0.01833279

model_1_svmRadial_FINAL <- model_1_svmRadial

```


### Fit to the test data 

```{r model_1_svm_predict, fig.width= 6, fig.height=5}

model_1_pred <- predict(model_1_svmRadial_FINAL,
                        newdata = test_set_1[, -1])

plt.df <- data.frame(pred = model_1_pred, obs = test_set_1[, 1])

## plot 1 
resid.tmp <- plt.df$obs - plt.df$pred
SS.total      <- sum((plt.df$obs - mean(plt.df$obs))^2)
SS.regression <- sum((plt.df$pred-mean(plt.df$obs))^2)
SS.residual   <- sum(resid.tmp^2)
r2.tmp <- SS.regression/SS.total
MSE.tmp <- mean((resid.tmp)^2)

ggplot(plt.df, aes(x = obs, y = pred)) + 
  geom_point() + 
  labs(title = paste0("Model predictions for y = log(# of downloads in 90 days) outcome on test set\n(red line: y = x)", 
                      "\nMSE: ", round(MSE.tmp, 3),
                      ", r^2: ", round(r2.tmp, 3)),
       x = "observed",
       y = "predicted") + 
  geom_abline(intercept = 0, slope = 1, color="red", 
              linetype="dashed", size=1.5) 


## plot 2
plt.df$resid <- resid.tmp
ggplot(plt.df, aes(x = obs, y = resid.tmp)) + 
  geom_point() + 
  labs(title = paste0("Model residuals for y = log(# of downloads in 90 days) outcome on test set\n(red line: y = 0)", 
                      "\nMSE: ", round(MSE.tmp, 3),
                      ", r^2: ", round(r2.tmp, 3)),
       x = "observed",
       y = "residual (y - hat{y})") + 
  geom_abline(intercept = 0, slope = 0, color="red", 
              linetype="dashed", size=1.5) 


```






