---
title: 'Modeling: support vector machine'
author: 
- "Perry Kuo"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: false
    toc_depth: 3
editor_options: 
  chunk_output_type: inline
---


```{r, include = FALSE}
rm(list = ls())
knitr::opts_chunk$set(include = TRUE, comment = NA, cache = TRUE, 
                      message = FALSE, warning = FALSE)

```

* Define project folder `712-final_project` path. That is, modify `project.dir` string below; once it points to your `712-final_project` folder location, all other stuff below would work. 

```{r}
user.name <- Sys.info()[7]
if(user.name=="antiporta") project.dir <- "/Users/antiporta/Dropbox/712-final_project/"
if(user.name=="mkaras") project.dir <- "/Users/mkaras/Dropbox/JHU/711-ADV_DATA_SCIENCE/712-final_project/"
if(user.name=="kuop2") project.dir <- "C:/Users/kuop2/Desktop/712-final_project"
if(user.name=="pkuo6") project.dir <- "C:/Users/pkuo6/Desktop/712-final_project"

library(caret)
library(dplyr)
library(reshape2)
library(ggplot2)
library(fastDummies)
library(janitor)
library(e1071)
library(kableExtra)
```


# Read data 

```{r}

out.path <- file.path(project.dir, "data/final_dfs/data_x.csv")
x_df0 <- read.csv(out.path, stringsAsFactors = FALSE)
# head(x_df0)

out.path <- file.path(project.dir, "data/final_dfs/data_y.csv")
y_df0 <- read.csv(out.path, stringsAsFactors = FALSE)
# head(y_df0)

```

# Mutate data 

### Create subset of columns of `x` data which will be used in modelling

```{r}
# apply(x_df0, 2, function(col) any(is.na(col)))
x_df0 <- 
  x_df0 %>% 
  select(-pkg_name,
         -rversion_min)

names(x_df0)[apply(x_df0, 2, function(col) any(is.na(col)))]
x_df0[is.na(x_df0)] <- 0
names(x_df0)[apply(x_df0, 2, function(col) any(is.na(col)))]
x_df <- x_df0
```


### Create dummy variables for subset of columns of `x`

```{r}
## x_df_license_group
x_df_license_group <- x_df %>% select(license_group)
x_df_license_group_DUMMY <- 
  dummy_cols(x_df_license_group,
             remove_most_frequent_dummy = TRUE) %>%
  select(-license_group)
x_df_license_group_DUMMY <- as.data.frame(clean_names(x_df_license_group_DUMMY))
x_df <- cbind(x_df %>% select(-license_group),
              x_df_license_group_DUMMY)
x_df <- scale(x_df, center = TRUE, scale = TRUE)
x_df <- as.data.frame(x_df)

## Sanity check
table(sapply(x_df, class))

```

### Mutate columns of `y` 

```{r}
y_df <- 
  y_df0 %>%
  select(-pkg_name) %>%
  mutate(download_cnt_90d_LOG = log(download_cnt_90d),
         download_cnt_365d_LOG = log(download_cnt_365d))
# y_df <- scale(y_df, center = TRUE, scale = TRUE)
y_df <- as.data.frame(y_df)

```


### Create data split 

```{r}
set.seed(56299)
trainIndex <- createDataPartition(y_df$download_cnt_90d, 
                                  p = 0.7, 
                                  list = FALSE, 
                                  times = 1)
head(trainIndex[, 1], 100)
mean(head(trainIndex[, 1], 100))

## Define the train and test set                                  
x_df_TRAIN <- x_df[trainIndex, ]
x_df_TEST  <- x_df[-trainIndex, ]
y_df_TRAIN <- y_df[trainIndex, ]
y_df_TEST  <- y_df[-trainIndex, ]

dim(x_df_TRAIN); dim(x_df_TEST)
dim(y_df_TRAIN); dim(y_df_TEST)

```



# Quickly explore the data 

```{r}
x_df.cor <- as.data.frame(cor(x_df))
x_df.cor$var1 <- rownames(x_df.cor)
x_df.cor <- x_df.cor %>% melt(id.vars = "var1")
## Create label 
x_df.cor_names_sorted <- as.data.frame(t(apply(x_df.cor[, 1:2], 1, sort))) 
x_df.cor_label <- paste0(x_df.cor_names_sorted[, 1], "_", x_df.cor_names_sorted[, 2])
x_df.cor$label <- x_df.cor_label
## Discard duplicates
x_df.cor.FINAL <- 
  x_df.cor %>%
  filter(var1 != variable) %>%
  select(label, value) %>%
  distinct() %>%
  arrange(desc(abs(value)))

boxplot(x_df.cor.FINAL$value, main = "Boxplot of correlation values")

```


# Model outcome: `download_cnt_90d_LOG`

- Model-specific objects

```{r}

## Data 
train_set_1 <- cbind(y_df_TRAIN %>% select(y = download_cnt_90d_LOG),
                     x_df_TRAIN)
train_set_1 <- cbind(y_df_TRAIN %>% select(y = download_cnt_90d_LOG),
                     x_df_TRAIN) %>%
                select(-license_group_epl, 
                       -license_group_acm,
                       -license_group_file_license,
                       -license_group_bsl,
                       -license_group_unlimited)
test_set_1 <- cbind(y_df_TEST %>% select(y = download_cnt_90d_LOG),
                    x_df_TEST)

## Control object
train_control <- trainControl(method = "repeatedcv", 
                              number = 10,
                              repeats = 10)

## svm problem: 
#???These variables have zero variances: license_group_epl, license_group_acm, license_group_file_licenseVariable(s) `' constant. Cannot scale data.
# These variables have zero variances: license_group_acm, license_group_file_licenseVariable(s) `' constant. Cannot scale data. 
# These variables have zero variances: license_group_acm, license_group_file_licenseVariable(s) `' constant. Cannot scale data.
# > sd(train_set_1$license_group_acm)
# [1] 0
# > mean(train_set_1$license_group_acm)
# [1] -0.02073903
# > head(train_set_1$license_group_acm)
# [1] -0.02073903 -0.02073903 -0.02073903 -0.02073903 -0.02073903 -0.02073903
t1 <- Sys.time()
## First model Model
svm_Linear01 <- train(y ~ . , data = train_set_1, 
                    method = "svmLinear",
                    preProcess = c("center"),
                    trControl=train_control)

svm_Linear01$results
#   C      RMSE   Rsquared       MAE   RMSESD RsquaredSD     MAESD
# 1 1 0.9079692 0.03678916 0.5152176 1.096092 0.03003147 0.1008808
t2 <- Sys.time()

t3 <- Sys.time()

svm_Linear200 <- train(y ~ . , data = train_set_1, 
                    method = "svmLinear",
                    preProcess = c("center"),
                    trControl=train_control,
                    tunelength = 200) 
t4 <- Sys.time()
# > svm_Linear200$results
#   C     RMSE   Rsquared      MAE  RMSESD RsquaredSD     MAESD
# 1 1 0.862489 0.03614399 0.509135 1.03422 0.02629914 0.1001996
# Take longer time with small improvement

t5 <- Sys.time()

grid <- expand.grid(C = 2^(0:9))
svm_Linear_grid <- train(y ~ . , data = train_set_1, 
                    method = "svmLinear",
                    preProcess = c("center"),
                    tuneGrid = grid,
                    trControl=train_control,tunelength = 200) 
t6 <- Sys.time()

svm_Linear_grid$results %>% 
  arrange(desc(-RMSE)) %>%
  kable() %>%
  kable_styling()

t2-t1
t4-t3
t6-t5

```



