---
title: 'Features engineering: task 1'
author: "Perry"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: false
    toc_depth: 3
---

- text features from package title         
- text features from package description      


```{r, include = FALSE}
rm(list = ls())
knitr::opts_chunk$set(include = TRUE, comment = NA, cache = FALSE, 
                      message = FALSE, warning = FALSE)
options(stringsAsFactors=FALSE)

```

* Define project folder `712-final_project` path. That is, modify `project.dir` string below; once it points to your `712-final_project` folder location, all other stuff below would work. 

```{r}

library(rvest)
library(ggplot2)
library(dplyr)
library(future)
library(stringi)
library(tm)
library(tools)

user.name<-Sys.info()[7]
if(user.name=="antiporta") project.dir <- "/Users/antiporta/Dropbox/712-final_project/"
if(user.name=="mkaras") project.dir <- "/Users/mkaras/Dropbox/JHU/711-ADV_DATA_SCIENCE/712-final_project"
if(user.name=="kuop2") project.dir <- "C:/Users/kuop2/Desktop/712-final_project"
```


# Read `data.frame` with package name, package first release 

```{r}
path.tmp <- file.path(project.dir, "data/pkg_first_release_SUBSET.csv")
pkg_first_rel <- read.csv(path.tmp, stringsAsFactors = FALSE)
pkg_first_rel$first_release <- as.Date(pkg_first_rel$first_release)

## Preview
head(pkg_first_rel)
```



# 1. Text features from package title/package description     
### Remarks


```{r}
packageNames.vec <- pkg_first_rel$pkg_name
pkg_first_rel$title <- NA
pkg_first_rel$description <- NA

t1 <- Sys.time()

as.integer(length(packageNames.vec)/100)

for(j in 1:as.integer(length(packageNames.vec)/100)){
  a <- j*100-99
  b <- j*100
  
  for(i in a:b){
  package <- read_html(paste0("https://cran.r-project.org/web/packages/",
                              packageNames.vec[i],
                              "/"))

  packagetitle1 <- package %>% 
    html_nodes("body h2") %>%
    html_text() %>%
    as.character()
  
  packagetitle2 <- package %>% 
    html_nodes("body p") %>%
    html_text() %>%
    as.character()  
  
  pkg_first_rel$title[i] <- packagetitle1[1]
  pkg_first_rel$description[i] <- packagetitle2[1]  
      
  }
  
}

t2 <- Sys.time()

t2 - t1

out.path <- file.path(project.dir, "data/pkg_text.csv")
write.csv(pkg_first_rel, out.path, row.names = FALSE, quote = FALSE)

```
