---
title: 'Features engineering: task 1'
author: 
- "Perry"
- "Marta"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: false
    toc_depth: 3
---

- text features from package title         
- text features from package description      


```{r, include = FALSE}
rm(list = ls())
knitr::opts_chunk$set(include = TRUE, comment = NA, cache = FALSE, 
                      message = FALSE, warning = FALSE)
options(stringsAsFactors=FALSE)

```

* Define project folder `712-final_project` path. That is, modify `project.dir` string below; once it points to your `712-final_project` folder location, all other stuff below would work. 

```{r}

library(rvest)
library(ggplot2)
library(dplyr)
library(future)
library(stringi)
library(tm)
library(tools)
library(utils)
library(tidytext)

user.name<-Sys.info()[7]
if(user.name=="antiporta") project.dir <- "/Users/antiporta/Dropbox/712-final_project/"
if(user.name=="mkaras") project.dir <- "/Users/mkaras/Dropbox/JHU/711-ADV_DATA_SCIENCE/712-final_project"
if(user.name=="kuop2") project.dir <- "C:/Users/kuop2/Desktop/712-final_project"
```


# Read `data.frame` with package name, package first release 

```{r}
path.tmp <- file.path(project.dir, "data/pkg_first_release_SUBSET.csv")
pkg_first_rel <- read.csv(path.tmp, stringsAsFactors = FALSE)
pkg_first_rel$first_release <- as.Date(pkg_first_rel$first_release)

## Preview
head(pkg_first_rel)
```


# Example of using tm to clean data and deal with plurals

- Assume tite / description is stored in a vector 

```{r}

titles.vec <- 
  c("Computing different outputs, especially the ones, which are nice, nicer of the nicest",
    "Computation of output 100x faster than all the previous packages &^*%*&^%",
    "The best package to compute anything out of all packages you can thinkg of!!!!!! j hdgfc 37456 37456lake")

```

### Create corpus: no cleaning yet done 

```{r}

corp <- Corpus(VectorSource(titles.vec))
dtm1 <- DocumentTermMatrix(corp)

## Function which converts DocumentTermMatrix object 
## to a nice matrix where rows are arranged as the `titles.vec`
## note: it uses tidytext library
dtm2mat <- function(dtm){
  mat <- 
    tidy(dtm) %>% 
    dcast(document ~ term, value.var = "count") %>% 
    arrange(document) %>%
    select(-document) %>%
    mutate_all(as.numeric) %>%
    as.matrix()
  mat[is.na(mat)] <- 0
  mat
}

dtm2mat(dtm1)

```


### Create corpus with cleaning (but no plural removed yet)

```{r}
corp2 <- 
  corp %>%
  tm_map(removePunctuation) %>%
  tm_map(content_transformer(tolower)) %>%
  tm_map(removeWords, c(stopwords("en"), "R")) %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)

dtm2mat(DocumentTermMatrix(corp2))

```

### Additionally remove plurals

```{r}
corp3 <- 
  corp2 %>%
  tm_map(stemDocument) 

dtm2mat(DocumentTermMatrix(corp3))

```


