---
title: 'Features engineering: task 1'
author: "Perry"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: false
    toc_depth: 3
---

- text features from package title         
- text features from package description      


```{r, include = FALSE}
rm(list = ls())
knitr::opts_chunk$set(include = TRUE, comment = NA, cache = TRUE, 
                      message = FALSE, warning = FALSE)
options(stringsAsFactors=FALSE)

```

* Define project folder `712-final_project` path. That is, modify `project.dir` string below; once it points to your `712-final_project` folder location, all other stuff below would work. 

```{r}
library(rvest)
library(ggplot2)
library(dplyr)
library(future)
library(stringi)
library(tm)
library(tools)
# library(qdap)
library(wordcloud)

user.name<-Sys.info()[7]
if(user.name=="antiporta") project.dir <- "/Users/antiporta/Dropbox/712-final_project/"
if(user.name=="mkaras") project.dir <- "/Users/mkaras/Dropbox/JHU/711-ADV_DATA_SCIENCE/712-final_project"
if(user.name=="kuop2") project.dir <- "C:/Users/kuop2/Desktop/712-final_project"
if(user.name=="pkuo6") project.dir <- "C:/Users/pkuo6/Desktop/712-final_project"
```


# Read `data.frame` with package name, package first release 

```{r}
path.tmp <- file.path(project.dir, "data/pkg_first_release_SUBSET.csv")
pkg_first_rel <- read.csv(path.tmp, stringsAsFactors = FALSE)
pkg_first_rel$first_release <- as.Date(pkg_first_rel$first_release)

## Preview
head(pkg_first_rel)
```



# 1. Text features from package title/package description     
### Remarks


```{r eval = FALSE}
packageNames.vec <- pkg_first_rel$pkg_name
pkg_first_rel$title <- NA
pkg_first_rel$description <- NA

t1 <- Sys.time()

for(i in 1:length(packageNames.vec)){


  package <- read_html(paste0("https://cran.r-project.org/web/packages/",
                              packageNames.vec[i],
                              "/"))
  packagetitle1 <- tryCatch({package %>% 
    html_nodes("body h2") %>%
    html_text() %>%
    as.character()}, error = function(e) { e })
    
  if (inherits(packagetitle1, "error")){
      pkg_first_rel$title[i] <- 
        "Unsuccessful package vignettes URL extract via html_nodes()"
    }else{
      pkg_first_rel$title[i] <- packagetitle1[1] 
    }

  packagetitle2 <- tryCatch({package %>% 
    html_nodes("body p") %>%
    html_text() %>%
    as.character()}, error = function(e) { e })
  if (inherits(packagetitle1, "error")){
      pkg_first_rel$description[i] <- 
        "Unsuccessful package vignettes URL extract via html_nodes()"
    }else{
      pkg_first_rel$description[i] <- packagetitle2[1] 
    }
  print(i)
}

t2 <- Sys.time()
t3 <- Sys.time()
t2 - t1
t3 - t1

out.path <- file.path(project.dir, "data/pkg_text2.csv")
write.csv(pkg_first_rel, out.path, row.names = FALSE, quote = FALSE)
out.path <- file.path(project.dir, "data/pkg_text2.rds")
saveRDS(pkg_first_rel, out.path, ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)

```
## Raw file for description     
```{r fig.height=10, fig.width=10}
path.tmp <- file.path(project.dir, "data/pkg_text2.rds")
titledescrip <- readRDS(path.tmp)

# Select the dataframe 
description_text <- titledescrip %>%
  select(pkg_name, description) %>%
  rename(doc_id = pkg_name,
         text = description) %>%
  data.frame(.)

# Build  corpus
df_source <- DataframeSource(description_text)
df_corpus <- VCorpus(df_source)
meta(df_corpus)

# Write a function on corpus
clean_corpus <- function(corpus) {
  # Remove punctuation
  corpus <- tm_map(corpus, removePunctuation)
  # Transform to lower case
  corpus <- tm_map(corpus, content_transformer(tolower))
  # Add more stopwords
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "R"))
  # Select stem
  corpus <- tm_map(corpus, stemDocument)
  # Remove numbers
  corpus <- tm_map(corpus, removeNumbers)
  # Remove punctuation
  corpus <- tm_map(corpus, removePunctuation)
  # Add more stopwords --> Do this again!
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "R","can","also"))
  # Strip whitespace
  corpus <- tm_map(corpus, stripWhitespace)
  return(corpus)
}

clean_df_corp <- clean_corpus(df_corpus)
description_dtm <- DocumentTermMatrix(clean_df_corp)
print(description_dtm) 
# Print out description_dtm data
# Really sparse!

description_m <- as.matrix(description_dtm)
dim(description_m)
description_m4csv <- cbind(pkg_name = titledescrip$pkg_name,description_m)

out.path <- file.path(project.dir, "data/pkg_description_raw_stem.csv")
write.csv(data.frame(description_m4csv), out.path)
out.path <- file.path(project.dir, "data/pkg_description_raw_stem.rds")
saveRDS(description_m, out.path, ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)

################# Plot
description_tdm <- TermDocumentMatrix(clean_df_corp)
description_m2 <- as.matrix(description_tdm)
term_frequency <- rowSums(description_m2)
term_frequency <- sort(term_frequency,
                       decreasing = TRUE)
barplot(term_frequency[1:20],
        col = "blue", las = 2)

forcloud <- data.frame(term = names(term_frequency),
                       num = term_frequency)
# make wordcloud
wordcloud(forcloud$term, forcloud$num,
          max.words = 100, colors = "red")

# Select final data
process = as.data.frame(description_m4csv)
forcloud_select = forcloud[forcloud$num > as.integer(nrow(titledescrip)*0.05),]
process_select = process[names(process) %in% c("pkg_name",as.character(forcloud_select$term))]

for(i in 1:length(names(process_select))){
  if(names(process_select)[i] == "pkg_name"){
    names(process_select)[i] = "pkg_name"
  } else{
    names(process_select)[i] = paste0("description_",names(process_select)[i])
  }
}

out.path <- file.path(project.dir, "data/pkg_description_extract.csv")
write.csv(data.frame(process_select), out.path,row.names = FALSE)
out.path <- file.path(project.dir, "data/pkg_description_extract.rds")
saveRDS(process_select, out.path, ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)
```


```{r words_histogram_description, fig.width=6, fig.height=6, cache = TRUE}

plt.df <- data.frame(term = names(term_frequency),
                       num = term_frequency)
plt.df <- 
  plt.df %>%
  arrange(desc(num)) %>%
  filter(row_number() <= 20 ) %>%
  arrange(num)
plt.df$term <- factor(as.character(plt.df$term),
                      levels = plt.df$term )

ggplot(plt.df, aes(x = term, y = num)) + 
  geom_bar(stat = "identity", fill = "blue", alpha = 0.5, color = "black") + 
  coord_flip() + 
  theme_minimal(base_size = 14) + 
  labs(x = "term", 
       y = "term count",
       title = "Term count across all packages description")
  

```


## Raw file for title     
```{r fig.height=10, fig.width=10}
path.tmp <- file.path(project.dir, "data/pkg_text2.rds")
titledescrip <- readRDS(path.tmp)

# Select the dataframe 
title_text <- titledescrip %>%
  select(pkg_name, title) %>%
  rename(doc_id = pkg_name,
         text = title) %>%
  data.frame(.)

# Build  corpus
df_source <- DataframeSource(title_text)
df_corpus <- VCorpus(df_source)
meta(df_corpus)

clean_corpus <- function(corpus) {
  # Remove punctuation
  corpus <- tm_map(corpus, removePunctuation)
  # Transform to lower case
  corpus <- tm_map(corpus, content_transformer(tolower))
  # Add more stopwords
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "R"))
  # Select stem
  corpus <- tm_map(corpus, stemDocument)
  # Remove numbers
  corpus <- tm_map(corpus, removeNumbers)
  # Remove punctuation
  corpus <- tm_map(corpus, removePunctuation)
  # Add more stopwords --> Do this again!
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "R","can","also"))
  # Strip whitespace
  corpus <- tm_map(corpus, stripWhitespace)
  return(corpus)
}

clean_df_corp <- clean_corpus(df_corpus)
title_dtm <- DocumentTermMatrix(clean_df_corp)
print(title_dtm) 
# Print out title_dtm data
# Really sparse!

title_m <- as.matrix(title_dtm)
dim(title_m)
title_m4csv <- cbind(pkg_name = titledescrip$pkg_name,title_m)

# Review a portion of the matrix 
# title_m[1208:1210, 758:779]

out.path <- file.path(project.dir, "data/pkg_title_raw.csv")
write.csv(data.frame(title_m4csv), out.path)
out.path <- file.path(project.dir, "data/pkg_title_raw.rds")
saveRDS(title_m, out.path, ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)

################# Plot
title_tdm <- TermDocumentMatrix(clean_df_corp)
title_m2 <- as.matrix(title_tdm)
term_frequency <- rowSums(title_m2)
term_frequency <- sort(term_frequency,
                       decreasing = TRUE)
barplot(term_frequency[1:20],
        col = "blue", las = 2)

forcloud <- data.frame(term = names(term_frequency),
                       num = term_frequency)
# make wordcloud
wordcloud(forcloud$term, forcloud$num,
          max.words = 100, colors = "red")

# Select final data
process = as.data.frame(title_m4csv)
# 0.01 = 1%
forcloud_select = forcloud[forcloud$num > as.integer(nrow(titledescrip)*0.01),]
process_select = process[names(process) %in% c("pkg_name",as.character(forcloud_select$term))]

for(i in 1:length(names(process_select))){
  if(names(process_select)[i] == "pkg_name"){
    names(process_select)[i] = "pkg_name"
  } else{
    names(process_select)[i] = paste0("title_",names(process_select)[i])
  }
}

out.path <- file.path(project.dir, "data/pkg_title_extract.csv")
write.csv(data.frame(process_select), out.path,row.names = FALSE)
out.path <- file.path(project.dir, "data/pkg_title_extract.rds")
saveRDS(process_select, out.path, ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)

```




```{r words_histogram_title, fig.width=6, fig.height=6, cache = TRUE}

plt.df <- data.frame(term = names(term_frequency),
                       num = term_frequency)
plt.df <- 
  plt.df %>%
  arrange(desc(num)) %>%
  filter(row_number() <= 20 ) %>%
  arrange(num)
plt.df$term <- factor(as.character(plt.df$term),
                      levels = plt.df$term )

ggplot(plt.df, aes(x = term, y = num)) + 
  geom_bar(stat = "identity", fill = "yellow", alpha = 0.5, color = "black") + 
  coord_flip() + 
  theme_minimal(base_size = 14) + 
  labs(x = "term", 
       y = "term count",
       title = "Term count across all packages title")
  

```
