---
title: 'Features engineering: Outcome'
author: 
- "Daniel Antiporta"
- "Marta Karas"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: false
    toc_depth: 3
---


```{r, include = FALSE}
rm(list = ls())
knitr::opts_chunk$set(include = TRUE, comment = NA, cache = TRUE, 
                      message = FALSE, warning = FALSE)

library(tidyverse)
library(reshape2)

```

* Define project folder `712-final_project` path. That is, modify `project.dir` string below; once it points to your `712-final_project` folder location, all other stuff below would work. 

```{r}
user.name<-Sys.info()[7]
if(user.name=="antiporta") project.dir <- "/Users/antiporta/Dropbox/712-final_project/"
if(user.name=="mkaras") project.dir <- "/Users/mkaras/Dropbox/JHU/711-ADV_DATA_SCIENCE/712-final_project/"
```


### Read `data.frame` with package name, package first release 

```{r}
path.tmp <- file.path(project.dir, "data/pkg_first_release_SUBSET.csv")
pkg_first_rel <- read.csv(path.tmp, stringsAsFactors = FALSE)
pkg_first_rel$first_release <- as.Date(pkg_first_rel$first_release)
  
## Sanity check
range(pkg_first_rel$first_release)
dim(pkg_first_rel)

## Preview
head(pkg_first_rel)
```

### Read `vector` with package name

```{r}
path.tmp <- file.path(project.dir, "data/pkg_name_SUBSET")
pkg_name_vec <- dget(path.tmp)

## Sanity check
length(pkg_name_vec)

## Preview
head(pkg_name_vec)
```

### Get information from ALL pkgs in the subset
```{r, eval=FALSE, message=FALSE, warning=FALSE}
#Get Downloads by Day 
#Pkg in Github to get info about downloads ["cranlogs"] (Option 1)
#NOTE: gives you data since the "from" point even if the pkg was not released, cross validation with date of first released.

if (!("cranlogs" %in% rownames(installed.packages()))){
  library(devtools)
  install_github("metacran/cranlogs")
}
library(cranlogs)


downloads.bydate.FINAL <- data.frame()
for (i in seq(1, 2301, by = 100)){
  message(i)
  idx <- i : min((i + 99), length(pkg_name_vec))
  downloads.bydate.i <- cran_downloads(pkg_name_vec[idx], 
                                       from = "2016-10-01", 
                                       to = "2018-10-31")
  downloads.bydate.FINAL <- rbind(downloads.bydate.FINAL, downloads.bydate.i)
  message(dim(downloads.bydate.FINAL))
}

#Sanity check
length(unique(downloads.bydate$package))

#Save
saveRDS(downloads.bydate.FINAL, 
        file = paste0(project.dir,
    "Rmd_files/2018-11-27-feature_task_outcome/downloads_pkgs_bydate"))

#Need to ADD date of First Release

#Pkg in CRAN to get info about downloads ["dlstats"] (Option 2) 
#[NOTE: it takes way more time than Option 1 and gives monthly data]
#if (!("dlstats" %in% rownames(installed.packages()))){
#  install.packages("dlstats")
#}
#library(dlstats)
#dlstats::cran_stats(pkg_name_vec)

```


# Generate outcome data frames

```{r}

file.path <- paste0(project.dir, "Rmd_files/2018-11-27-feature_task_outcome/downloads_pkgs_bydate")
downloads_pkgs <- read_rds(file.path)
names(downloads_pkgs) <- c("download_date", "download_cnt", "pkg_name")

dim(downloads_pkgs)
head(downloads_pkgs)
range(downloads_pkgs$download_date)

outcome.df0 <- 
  pkg_first_rel %>% 
  left_join(downloads_pkgs, by= "pkg_name") %>%
  mutate(release_download_diff = as.numeric(as.Date(download_date) - as.Date(first_release), units = "days")) %>%
  filter(release_download_diff >= 0, release_download_diff <= 365)

## Sanity check (that we have same num of observations per package)
unique(table(outcome.df0$pkg_name))

```


## Some exploratory plots

### Aggregate per 90 days and per 365 days

```{r}
outcome.df_90 <- 
  outcome.df0 %>%
  filter(release_download_diff <= 90) %>%
  group_by(pkg_name) %>%
  summarize(download_cnt_90d = sum(download_cnt))

outcome.df_365 <- 
  outcome.df0 %>%
  filter(release_download_diff <= 365) %>%
  group_by(pkg_name) %>%
  summarize(download_cnt_365d = sum(download_cnt))

outcome.df <- 
  pkg_first_rel %>%
  left_join(outcome.df_90, by = "pkg_name") %>%
  left_join(outcome.df_365, by = "pkg_name") %>%
  select(-first_release)

```


```{r EDA_outcome, fig.width=5, fig.height=4}

gg.base_size <- 10

outcome.df.m <-
  outcome.df %>%
  select(download_cnt_90d, download_cnt_365d) %>%
  melt()

ggplot(outcome.df.m, aes(x = variable, y = value)) + 
  geom_boxplot() + 
  labs(title = "Boxplot of # downloads over time window (90/365 days)",
       x = "Outcome variable") + 
  theme_gray(base_size = gg.base_size) 

ggplot(outcome.df.m, aes(x = variable, y = value)) + 
  geom_boxplot() + 
  labs(title = "Boxplot of # downloads over time window (90/365 days)\n(y-axis limited)",
       x = "Outcome variable") + 
    coord_cartesian(ylim = c(0, 30000)) +  
  theme_gray(base_size = gg.base_size)

ggplot(outcome.df.m, aes(x = variable, y = log(value))) + 
  geom_boxplot() + 
  labs(title = "Boxplot of log(# downloads) over time window (90/365 days)",
       x = "Outcome variable") +   
  theme_gray(base_size = gg.base_size)


```


## Save outcome data frames

```{r, eval = FALSE}

out.path <- file.path(project.dir, "data/final_dfs/data_y.csv")
write.csv(outcome.df, out.path, row.names = FALSE, quote = FALSE)

## construct common data frame for all the past ones 
dir.path <- file.path(project.dir, "data/feature_task/")
dir.list.files <- list.files(dir.path, full.names = TRUE)

dim.sum <- 0
for (file.path.i in dir.list.files){
  message(file.path.i)
  file.i <- read.csv(file.path.i, stringsAsFactors = FALSE)
  print(dim(file.i))
  print(head(file.i))
  dim.sum <- dim.sum + dim(file.i)[2]
}
dim.sum

## Combine all these 

df.X.FINAL <- pkg_first_rel 
for (file.path.i in dir.list.files){
  message(file.path.i)
  file.i <- read.csv(file.path.i, stringsAsFactors = FALSE)
  df.X.FINAL <- 
    df.X.FINAL %>%
    left_join(file.i, by = "pkg_name")
    print(dim(df.X.FINAL))
}

df.X.FINAL <- df.X.FINAL %>% select(-first_release)


out.path <- file.path(project.dir, "data/final_dfs/data_x.csv")
write.csv(df.X.FINAL, out.path, row.names = FALSE, quote = FALSE)

```






